---
title: "AXYS Project Grant: Sensitivity analyses and linear modelling"
author: "Angela Ching"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: yes
---

# Notes from MH

IsletCore GSIS:
- Condition #1 = LG 2.8mM, HG 16.7mM 
- Condition #2 = LG 1mM, HG 16.7mM
- Condition #3 = LG 1mM, HG 10mM

Perifusion:
- Exclude KCl for donors: R361, R362, R385, R391 (already removed from final excel)
- Only use basal LG (exclude the rest of perifusion curve) for donors: R419, R421 (already removed from final excel)
- Do sensitivity analysis with donor R417

Exclusion criteria
- Remove any analyte with >50% donors below LOD
- Remove any analyte with >40% of donors with NDR flag

```{r}
# Get today's date for saving plots
date_today <- Sys.Date()
```

# Packages

```{r packages}
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)      # for data cleaning
library(scico)        # colour palettes
library(ggsci)        # colour palettes
library(ggpubr)       # for scatterplot correlations
library(psychometric) # masks "select" from dplyr; for CIr()
library(purrr)        # for mapping heatmaps
library(reshape2)     # for reshaping data for heatmaps
library(knitr)
library(pheatmap)
library(corrplot)
library(psych)
library(lme4)
library(moments)
library(gridExtra)
```

# Sensitivity analyses

## Load data

```{r}
# Combine all correlation files into one dataframe
compiled_outputs <- suppressWarnings(
  map_dfr(.x = list.files(path = "../../outputs/2024-10-02_ProjectGrant_sensitivity_analyses",
                                      recursive = TRUE,
                                      pattern = ".csv",
                                      full.names = TRUE),
          .f = ~read_csv(.x) %>%
            dplyr::mutate(Filename = str_remove(basename(.x), ".csv")),
          
          # Add a number to identify which rows came from the same file
          .id = "File"))

compounds_n <- read_xlsx(path = "../../data/2024-10-03_List_of_compounds_with_sample_size.xlsx") %>%
  mutate(across(c(4:ncol(.)), as.numeric))

# compounds_n_panc <- compounds_n %>%
#   dplyr::filter(TISSUE_TYPE == "Pancreas") %>%
#   dplyr::select(-n_rm_421)
# 
# compounds_n_adip <- compounds_n %>%
#   dplyr::filter(TISSUE_TYPE == "Adipose") %>%
#   dplyr::select(-c(n_rm_389, n_rm_448))

pops_rchange <- compiled_outputs %>%
  dplyr::select(-2) %>%
  mutate(Comparison = case_when(str_detect(Filename, pattern = "analyte-to-metadata") ~ "analyte_vs_metadata",
                                str_detect(Filename, pattern = "gsis") ~ "analyte_vs_gsis",
                                str_detect(Filename, pattern = "perifusion") ~ "analyte_vs_gsis"),
         Pollutant_class = case_when(str_detect(Filename, pattern = "dioxin") ~ "Dioxin",
                                str_detect(Filename, pattern = "pcb") ~ "PCB",
                                str_detect(Filename, pattern = "ocp") ~ "OCP"),
         Tissue_type = case_when(str_detect(Filename, pattern = "panc") ~ "Pancreas",
                                str_detect(Filename, pattern = "adip") ~ "Adipose"),
         GSIS_type = case_when(str_detect(Filename, pattern = "IsletCore") ~ "IsletCore_static_GSIS",
                               str_detect(Filename, pattern = "JK_glu") ~ "JK_glucose_perifusion",
                               str_detect(Filename, pattern = "JK_leu") ~ "JK_leucine_perifusion",
                               str_detect(Filename, pattern = "JK_fatty_acid") ~ "JK_fatty_acid_perifusion",
                               str_detect(Filename, pattern = "MH") ~ "MH_glucose_perifusion"),
         Correction_type = case_when(str_detect(Filename, pattern = "imput") ~ "imputation",
                               str_detect(Filename, pattern = "removing_all_outlier") ~ "removed_all_outlier_donors",
                               str_detect(Filename, pattern = "R389") ~ "removed_R389",
                               str_detect(Filename, pattern = "R419") ~ "removed_R419",
                               str_detect(Filename, pattern = "R421") ~ "removed_R421",
                               str_detect(Filename, pattern = "R448") ~ "removed_R448")) %>%
  relocate(File, Tissue_type, Comparison, Pollutant_class, GSIS_type, Correction_type)


pops_rchange_n <- pops_rchange %>%
  left_join(., compounds_n, by = c("Tissue_type" = "TISSUE_TYPE", "column" = "COMPOUND")) %>%
  left_join(., compounds_n, by = c("Tissue_type" = "TISSUE_TYPE", "row" = "COMPOUND")) %>%
  mutate(n = coalesce(n.x, n.y),
         n_rm_all = coalesce(n_rm_all.x, n_rm_all.y),
         n_rm_389 = coalesce(n_rm_389.x, n_rm_389.y),
         n_rm_419 = coalesce(n_rm_419.x, n_rm_419.y),
         n_rm_421 = coalesce(n_rm_421.x, n_rm_421.y),
         n_rm_448 = coalesce(n_rm_448.x, n_rm_448.y),
         .keep = c("unused")) %>%
  dplyr::select(-c(Type.x, Type.y))
```

## Calculate range change in r

```{r}
summary_rchange <- pops_rchange_n %>%
  group_by(File, Tissue_type, Comparison, Pollutant_class, GSIS_type, Correction_type) %>%
  summarise(
    r_min = min(r_difference, na.rm = TRUE),
    r_max = max(r_difference, na.rm = TRUE)
  )
```

```{r}
# Filter only r changes > 0.1
pops_rdiff_filt <- pops_rchange %>%
  dplyr::filter(r_difference > 0.1)
```

## Statistical testing

```{r}
##### Need to separate files by analysis Correction_type ######
correction_type <- pops_rchange_n %>%
  distinct(Correction_type) %>%
  pull(Correction_type)

pops_rchange_panc <- pops_rchange_n %>%
  dplyr::filter(Tissue_type == "Pancreas")

pops_rchange_adip <- pops_rchange_n %>%
  dplyr::filter(Tissue_type == "Adipose")

adip_rm_421 <- pops_rchange_adip %>%
  rowwise() %>%
  mutate(
    z_initial = 0.5 * log((1 + r_initial) / (1 - r_initial)),
    z_new = 0.5 * log((1 + r_new) / (1 - r_new)),
    z_diff = abs(z_initial - z_new),
    se = sqrt(1 / (n - 3) + 1 / (n_rm_421 - 3)),  # Assuming you have n_initial and n_new as sample sizes
    z_stat = z_diff / se,
    p_value = 2 * pnorm(-abs(z_stat))  # Two-tailed test
  ) %>%
  dplyr::filter(p_value < 0.05)
```

# Linear modelling

## Load AXYS pollutant concentration data and metadata

```{r}
# load AXYS data
axys_pops <- read_csv("../../outputs/2024-08-24_ProjectGrant_excluded_outliers_for_single_analyte_analyses.csv") %>%
  dplyr::select(-c(CONC_BLANK_adj, IS_BLANK_ADJ_CONC_HIGHER_THAN_LOD)) %>%
  mutate(BLANK_and_LOD_adj = as.numeric(BLANK_and_LOD_adj),
         File = factor(File),
         COMPOUND = case_when(str_detect(COMPOUND, "TOTAL") ~ str_to_sentence(COMPOUND),
                              str_detect(COMPOUND, " Epoxide") ~ str_to_sentence(COMPOUND),
                              TRUE ~ COMPOUND),
         across(where(is.character), str_squish))

axys_pops_2 <- axys_pops %>%
  dplyr::select(-c(File, LAB_FLAG, DETECTION_LIMIT)) %>%
  mutate(across(where(is.character), str_squish),
         COMPOUND = make.names(COMPOUND),
         COMPOUND = str_replace_all(COMPOUND, "\\.", "_"),
         COMPOUND = str_replace_all(COMPOUND, "__+", "_"))

# load chemical list
chem_list <- read_csv("../../data/2022-10-18_AXYS_chemicals_list_AC.csv") %>%
  dplyr::select(Compound, Dioxin_subtype) %>%
  mutate(across(where(is.character), str_squish))

# chem_list_2 <- read_csv("../../data/2024-10-01_AXYS_chemicals_list_with_coelutions.csv") %>%
#   dplyr::select(-c(Dioxin_subtype, Type)) %>%
#   mutate(across(where(is.character), str_squish),
#          Compound = make.names(Compound))

chem_list_2 <- read_csv("../../data/2024-10-01_AXYS_chemicals_list_with_coelutions.csv") %>%
  dplyr::select(-c(Dioxin_subtype, Type, Compound_rename)) %>%
  mutate(across(where(is.character), str_squish),
         Compound = make.names(Compound),
         Compound = str_replace_all(Compound, "\\.", "_"),
         Compound = str_replace_all(Compound, "__+", "_"))

# load AXYS donor metadata
axys_metadata <- read_csv("../../data/2024-08-22_donor_characteristics_FINAL.csv", show_col_types = FALSE) %>%
  mutate(BMI_category = case_when(BMI < 24.9 ~ "Lean",
                                  BMI >= 24.9 & BMI <= 29.9 ~ "Overweight",
                                  BMI > 29.9 ~ "Obese"),
         Hba1c_category = case_when(Hba1c < 6 ~ "Normoglycemic",
                                    Hba1c <= 6.5 ~ "Prediabetic",
                                    Hba1c > 6.5 ~ "Diabetic"),
         BMI_category = factor(BMI_category, levels = c("Lean", "Overweight", "Obese")),
         Hba1c_category = factor(Hba1c_category, levels = c("Normoglycemic", "Prediabetic", "Diabetic")),
         Sex = as_factor(Sex),
         Diabetes_status = as_factor(Diabetes_status)) %>%
  dplyr::select(-Purity)

# Donor IDs
axys_donors <- axys_metadata %>%
  dplyr::select(Id)

# Main correlations to explore with linear model corrections
axys_main_corr <- read_excel("../../data/2024-11-07_ComparisonList_AXYS_linear_models_adjustments.xlsx", sheet = 1) %>%
  dplyr::select(-Comparison_with)

# Subset data by tissue type
subset_tissue <- function(tissue) {
  axys_pops_2 %>%
    dplyr::filter(!str_detect(COMPOUND, "Total"), TISSUE_TYPE == tissue) %>%
    dplyr::select(DONOR, COMPOUND, BLANK_and_LOD_adj) %>%
    group_by(DONOR) %>%
    pivot_wider(names_from = COMPOUND, values_from = BLANK_and_LOD_adj) %>%
    ungroup()
}

axys_pops_panc <- subset_tissue("Pancreas")
axys_pops_adip <- subset_tissue("Adipose")
```

```{r}
# Calculate sums
axys_panc_sums <- axys_pops_panc %>%
  pivot_longer(cols = c(2:ncol(.)), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("Dioxin-like", "Non-dioxin-like")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

axys_adip_sums <- axys_pops_adip %>%
  pivot_longer(cols = c(2:ncol(.)), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("Dioxin-like", "Non-dioxin-like")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()
```

## Transform data

```{r}
transform_column <- function(col, method = "log2") {
  if (method == "log2") {
    return(log2(col + 1))  # Adding 1 to handle zero values if needed
  } else if (method == "sqrt") {
    return(sqrt(col))
  } else if (method == "boxcox") {
    # Check for negative values, as Box-Cox requires positive data
    if (all(col > 0)) {
      lambda <- MASS::boxcox(lm(col ~ 1), plot = FALSE)$x[which.max(MASS::boxcox(lm(col ~ 1), plot = FALSE)$y)]
      return((col ^ lambda - 1) / lambda)
    } else {
      warning("Box-Cox transformation requires positive values")
      return(col)
    }
  } else {
    stop("Unknown transformation method")
  }
}
```

```{r}
library(purrr)
library(ggplot2)
library(moments)

# Define a function to check transformations for each column
check_distribution <- function(df) {
  
  # Helper function to plot and run checks for a single variable
  analyze_column <- function(col_data, col_name) {
    # Create histogram using tidy evaluation
    hist_plot <- ggplot(df, aes(x = !!rlang::sym(col_name))) + 
      geom_histogram(bins = 30, fill = "lightblue", color = "black") +
      labs(title = paste("Histogram of", col_name))
    
    # Create Q-Q plot using tidy evaluation
    qq_plot <- ggplot(df, aes(sample = !!rlang::sym(col_name))) +
      stat_qq() + stat_qq_line() +
      labs(title = paste("Q-Q Plot of", col_name))
    
    # Shapiro-Wilk test for normality
    shapiro_result <- tryCatch({
      shapiro_test <- shapiro.test(col_data)
      list(statistic = shapiro_test$statistic, p.value = shapiro_test$p.value)
    }, error = function(e) {
      list(statistic = NA, p.value = NA)  # Handle errors (e.g., for non-numeric columns)
    })
    
    # Skewness and Kurtosis
    skewness_val <- tryCatch(skewness(col_data, na.rm = TRUE), error = function(e) NA)
    kurtosis_val <- tryCatch(kurtosis(col_data, na.rm = TRUE), error = function(e) NA)
    
    # Output results
    list(
      hist_plot = hist_plot,
      qq_plot = qq_plot,
      shapiro_result = shapiro_result,
      skewness = skewness_val,
      kurtosis = kurtosis_val
    )
  }
  
  # Select numeric columns and apply analysis with named results
  numeric_cols <- df %>% select_if(is.numeric)
  
  # Use purrr::imap to retain column names in the output list
  results <- purrr::imap(numeric_cols, ~ analyze_column(.x, .y))
  
  return(results)
}

# Access and display results for a specific column, e.g., PCB1
results[["PCB1"]][["hist_plot"]]
results[["PCB1"]][["qq_plot"]]
results[["PCB1"]][["shapiro_result"]]
results[["PCB1"]][["skewness"]]
results[["PCB1"]][["kurtosis"]]
```

```{r, fig.width=20}
library(gridExtra)

# Function to display all histograms and Q-Q plots
output_plots <- function(results) {
  
  # Loop through results and extract the plots
  plots_list <- map(results, function(res) {
    list(
      hist_plot = res$hist_plot,
      qq_plot = res$qq_plot
    )
  })
  
  # Flatten the list of plots for easier display
  all_hist_plots <- map(plots_list, "hist_plot")
  all_qq_plots <- map(plots_list, "qq_plot")
  
  # Display histograms
  print("Histograms:")
  grid.arrange(grobs = all_hist_plots, ncol = 5)  # Adjust ncol for desired layout
  
  # Display Q-Q plots
  print("Q-Q Plots:")
  grid.arrange(grobs = all_qq_plots, ncol = 5)  # Adjust ncol for desired layout
}

```

```{r}
# Combine single analyte concentrations with sums
axys_pops_with_sums_panc <- axys_pops_panc %>%
  left_join(., axys_panc_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip <- axys_pops_adip %>%
  left_join(., axys_adip_sums, by = c("DONOR" = "DONOR"))
```

```{r}
# Transform data
axys_pops_panc_log <- axys_pops_with_sums_panc %>%
  mutate(across(where(is.numeric), ~ transform_column(., method = "log2")))

axys_pops_adip_log <- axys_pops_with_sums_adip %>%
  mutate(across(where(is.numeric), ~ transform_column(., method = "log2")))
```

```{r, fig.width=20}
# Check plots without any transformations
axys_pops_panc_res <- check_distribution(axys_pops_panc)
axys_pops_adip_res <- check_distribution(axys_pops_adip)

# Output plots
output_plots(axys_pops_panc_res)
output_plots(axys_pops_adip_res)

# Check transformations after log-transforming
axys_pops_panc_log_res <- check_distribution(axys_pops_panc_log)
axys_pops_adip_log_res <- check_distribution(axys_pops_adip_log)

# Output plots
output_plots(axys_pops_panc_log_res)
output_plots(axys_pops_adip_log_res)

```

```{r}
# Combine single analyte concentrations and sums with metadata
axys_pops_with_sums_panc_meta <- axys_pops_panc_log %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta <- axys_pops_adip_log %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)
```

## Load static GSIS and perifusion data

```{r}
# load GSIS data from ADI
gsis_adi_all_ave <- read_excel("../../data/Perifusion+GSIS/2024-05-18_IsletCore_GSIS_from_TeamGrant_website.xlsx") %>%
  dplyr::mutate_at(c(4:7), as.numeric) %>%
  group_by(Donor, Cond) %>%
  dplyr::mutate(Cond = factor(Cond, levels = c("1", "2", "3")),
                InsulinContent_IsletCore = mean(InsulinContent),
                LG_IsletCore = mean(LG, na.rm = TRUE),
                HG_IsletCore = mean(HG, na.rm = TRUE),
                SI_IsletCore = mean(SI, na.rm = TRUE),
                .keep = c("unused")) %>%
  distinct(Donor, Cond, .keep_all = TRUE) %>%
  dplyr::select(-replicate) %>%
  ungroup()
  
gsis_adi <- gsis_adi_all_ave %>%
  pivot_wider(names_from = Cond, values_from = c(InsulinContent_IsletCore, LG_IsletCore, HG_IsletCore, SI_IsletCore)) %>%
  relocate(Donor, InsulinContent_IsletCore_1, LG_IsletCore_1, HG_IsletCore_1, SI_IsletCore_1,
           InsulinContent_IsletCore_2, LG_IsletCore_2, HG_IsletCore_2, SI_IsletCore_2,
           InsulinContent_IsletCore_3, LG_IsletCore_3, HG_IsletCore_3, SI_IsletCore_3)
```

```{r}
# Load perifusion data from Jelena Kolic
peri_jk <- read_excel("../../data/Perifusion+GSIS/2024-04-06_Jelena_all_perifusion_AUCs.xlsx") %>%
 dplyr::mutate(PerifusionParam = str_c("JK", PerifusionParam, sep = "_"),
         .keep = "unused") %>% 
  dplyr::mutate_at(c(4:148), as.numeric)

# Separate data based on perifusion type (glucose, leucine, oleate-pamlitate)
glu_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "GLU") %>%
  remove_empty("cols")

leu_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "LEU") %>%
  remove_empty("cols")

fa_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "OLE-PALM") %>%
  remove_empty("cols")

# Transpose for matrices
glu_peri_jk_t <- glu_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  mutate_at(c(2:20), as.numeric)

leu_peri_jk_t <- leu_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  mutate_at(c(2:12), as.numeric)

fa_peri_jk_t <- fa_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  mutate_at(c(2:12), as.numeric)
```

```{r}
# Load Myriam perifusion data
glu_peri_mh <- read_excel("../../data/Perifusion+GSIS/2024-01-25_Perifusion_FINAL DATA_For analysis_AC.xlsx") %>%
  mutate(PerifusionParam = str_c("MH", PerifusionParam, sep = "_"),
         .keep = c("unused")) %>% 
  dplyr::mutate_at(c(3:32), as.numeric)

glu_peri_mh_t <- glu_peri_mh %>%
  dplyr::select(-MainOutcome) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor)
```

## Combine pollutant concentration data with other data types

```{r}
axys_adi_gsis_panc <- axys_pops_with_sums_panc_meta %>%
  left_join(gsis_adi, by = c("DONOR" = "Donor"))

axys_adi_gsis_adip <- axys_pops_with_sums_adip_meta %>%
  left_join(gsis_adi, by = c("DONOR" = "Donor"))

axys_glu_peri_jk_panc <- axys_pops_with_sums_panc_meta %>%
  left_join(glu_peri_jk_t, by = c("DONOR" = "Donor"))

axys_glu_peri_jk_adip <- axys_pops_with_sums_adip_meta %>%
  left_join(glu_peri_jk_t, by = c("DONOR" = "Donor"))

axys_leu_peri_jk_panc <- axys_pops_with_sums_panc_meta %>%
  left_join(leu_peri_jk_t, by = c("DONOR" = "Donor"))

axys_leu_peri_jk_adip <- axys_pops_with_sums_adip_meta %>%
  left_join(leu_peri_jk_t, by = c("DONOR" = "Donor"))

axys_fa_peri_jk_panc <- axys_pops_with_sums_panc_meta %>%
  left_join(fa_peri_jk_t, by = c("DONOR" = "Donor"))

axys_fa_peri_jk_adip <- axys_pops_with_sums_adip_meta %>%
  left_join(fa_peri_jk_t, by = c("DONOR" = "Donor"))

axys_glu_peri_mh_panc <- axys_pops_with_sums_panc_meta %>%
  left_join(glu_peri_mh_t, by = c("DONOR" = "Donor"))

axys_glu_peri_mh_adip <- axys_pops_with_sums_adip_meta %>%
  left_join(glu_peri_mh_t, by = c("DONOR" = "Donor"))


axys_adi_gsis_panc <- axys_pops_with_sums_panc_meta %>%
  left_join(gsis_adi, by = c("DONOR" = "Donor"))

axys_func_dfs_panc <- list(axys_pops_with_sums_panc_meta, gsis_adi, glu_peri_jk_t, leu_peri_jk_t, fa_peri_jk_t, glu_peri_mh_t)

axys_func_dfs_adip <- list(axys_pops_with_sums_adip_meta, gsis_adi, glu_peri_jk_t, leu_peri_jk_t, fa_peri_jk_t, glu_peri_mh_t)

axys_func_all_panc <- reduce(axys_func_dfs_panc, left_join, by = c("DONOR" = "Donor"))
axys_func_all_adip <- reduce(axys_func_dfs_adip, left_join, by = c("DONOR" = "Donor"))
```

```{r}
# Create compounds list
sum_dioxin <- data.frame(Compound = "Dioxin", Dioxin_similarity = "Dioxin")
sum_pcb <- data.frame(Compound = c("PCB", "Dioxin-like", "Non-dioxin-like"), Dioxin_similarity = c("Dioxin-like", "Dioxin-like", "Non-dioxin-like"))

dioxin_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin") %>%
  bind_rows(sum_dioxin) %>%
  dplyr::pull(Compound)

pcb_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin-like" | Dioxin_similarity == "Non-dioxin-like") %>%
  bind_rows(sum_pcb) %>%
  dplyr::pull(Compound)

ocp_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "OCP") %>%
  dplyr::pull(Compound)
```

```{r}
# Functional parameters
gsis_adi_param <- colnames(gsis_adi)[2:ncol(gsis_adi)]
glu_peri_jk_param <- colnames(glu_peri_jk_t)[2:ncol(glu_peri_jk_t)]
leu_peri_jk_param <- colnames(leu_peri_jk_t)[2:ncol(leu_peri_jk_t)]
fa_peri_jk_param <- colnames(fa_peri_jk_t)[2:ncol(fa_peri_jk_t)]
glu_peri_mh_param <- colnames(glu_peri_mh_t)[2:ncol(glu_peri_mh_t)]
```


```{r}
library(purrr)

# Define your pollutants and functional outputs
# pollutants <- chem_list_2 %>%
#   bind_rows(sum_dioxin, sum_pcb) %>%
#   dplyr::pull(Compound)

pollutants <- chem_list_2 %>%
  bind_rows(sum_pcb, sum_dioxin) %>%
  dplyr::pull(Compound)

functional_outputs <- c(gsis_adi_param, glu_peri_jk_param, leu_peri_jk_param, fa_peri_jk_param, glu_peri_mh_param)

```

```{r}
# Helper function to safely wrap variable names with backticks if needed
safe_var <- function(var_name) {
  if (grepl("[^[:alnum:]_]", var_name)) {
    return(paste0("`", var_name, "`"))
  } else {
    return(var_name)
  }
}

# List of covariates (including an option for no covariates)
covariate_combinations <- list(
  "None" = character(0),  # No covariates
  "BMI" = c("BMI"),
  "Age" = c("Age"),
  "Sex" = c("Sex"),
  "Age_BMI" = c("Age", "BMI")
)

# Define a function that fits models
fit_model <- function(df, func, pollutant, covariates) {
  # Make variable names safe for formula
  func_safe <- safe_var(func)
  pollutant_safe <- safe_var(pollutant)
  
  # Construct the formula, accounting for the case of no covariates
  if (length(covariates) == 0) {
    formula <- as.formula(paste0(func_safe, " ~ ", pollutant_safe))
  } else {
    formula <- as.formula(paste0(func_safe, " ~ ", pollutant_safe, " + ", paste(covariates, collapse = " + ")))
  }

  # Fit the model only if columns exist in the dataframe
  if (all(c(func, pollutant) %in% colnames(df))) {
    lm(formula, data = df)
  } else {
    warning(paste("Column", func, "or", pollutant, "not found in dataframe."))
    return(NULL)
  }
}

# Fit models
fit_all_models <- function(df) {
  # Filter pollutants and functional outputs to only those present in df
  available_pollutants <- pollutants[pollutants %in% colnames(df)]
  available_outputs <- functional_outputs[functional_outputs %in% colnames(df)]
  
  # Create combinations using only available pollutants and functional outputs
  combinations <- expand_grid(available_outputs, available_pollutants)
  
  # Fit all models
  models <- combinations %>%
    pmap(~ {
      func <- ..1
      pollutant <- ..2
      
      # Fit models for each covariate combination
      map(covariate_combinations, ~ fit_model(df, func, pollutant, .x))
    })
  
  # Name the models for easier access
  model_names <- combinations %>%
    mutate(name = paste(available_outputs, available_pollutants, sep = "__")) %>%
    pull(name)
  
  names(models) <- model_names
  
  return(models)
}

# Updated fit_all_models function with comparison metrics
fit_models_metrics <- function(df) {
  # Filter pollutants and functional outputs to only those present in df
  available_pollutants <- pollutants[pollutants %in% colnames(df)]
  available_outputs <- functional_outputs[functional_outputs %in% colnames(df)]
  
  # Define a list of covariate combinations, including "no covariates" option
  full_covariate_combinations <- c(list("None" = NULL), covariate_combinations)
  
  # Create combinations using only available pollutants and functional outputs
  combinations <- expand_grid(func = available_outputs, pollutant = available_pollutants)
  
  # Fit models and calculate comparison metrics
  model_metrics <- combinations %>%
    pmap_df(~ {
      func <- ..1
      pollutant <- ..2
      
      # Fit models with each covariate combination and store metrics
      metrics <- map_dfr(names(full_covariate_combinations), function(covar_name) {
        covars <- full_covariate_combinations[[covar_name]]  # Get covariates
        
        model <- fit_model(df, func, pollutant, covars)
        
        if (!is.null(model)) {
          tibble(
            functional_output = func,
            pollutant = pollutant,
            covariates = covar_name,
            AIC = AIC(model),
            adj_r_squared = summary(model)$adj.r.squared
          )
        } else {
          # Return NA for cases where the model couldn't be fit
          tibble(
            functional_output = func,
            pollutant = pollutant,
            covariates = covar_name,
            AIC = NA,
            adj_r_squared = NA
          )
        }
      })
      
      metrics
    })
  
  return(model_metrics)
}
# Accessing a specific model (e.g., high_glucose and PCB1 with BMI as covariate)
#summary(models[["high_glucose_PCB1"]][["BMI"]])
```

```{r}
library(dplyr)
library(tidyr)
library(purrr)

summarize_models <- function(models) {
  # Initialize an empty list to collect all summaries
  model_summaries <- imap_dfr(models, ~ {
    # Split .y into functional_output and pollutant before proceeding
    components <- strsplit(.y, "__")[[1]]
    functional_output <- components[1]  # First part
    pollutant <- paste(components[-1], collapse = "__")  # Everything after the first part, combined back
    
    map_dfr(.x, function(model, covar_name) {
      # Attempt to extract summary statistics
      summary_result <- tryCatch({
        if (!is.null(model)) {
          summary_model <- summary(model)
          
          # Check if the coefficients are available
          if (!is.null(summary_model$coefficients) && is.matrix(summary_model$coefficients)) {
            tibble(
              term = rownames(summary_model$coefficients),
              estimate = summary_model$coefficients[, "Estimate"],
              std_error = summary_model$coefficients[, "Std. Error"],
              p_value = summary_model$coefficients[, "Pr(>|t|)"],
              r_squared = summary_model$r.squared,
              adj_r_squared = summary_model$adj.r.squared,
              AIC = AIC(model),
              residual_std_error = summary_model$sigma,  # Residual standard error
              f_statistic = summary_model$fstatistic[1], # F-statistic
              model_p_value = pf(summary_model$fstatistic[1], 
                                 summary_model$fstatistic[2], 
                                 summary_model$fstatistic[3], 
                                 lower.tail = FALSE) # p-value of F-statistic
            )
          } else {
            # If no coefficients, return NA row
            tibble(term = NA, estimate = NA, std_error = NA, p_value = NA, 
                   r_squared = NA, adj_r_squared = NA, AIC = AIC(model),
                   residual_std_error = NA, f_statistic = NA, model_p_value = NA)
          }
        } else {
          # Return empty row for missing model
          tibble(term = NA, estimate = NA, std_error = NA, p_value = NA, 
                 r_squared = NA, adj_r_squared = NA, AIC = NA,
                 residual_std_error = NA, f_statistic = NA, model_p_value = NA)
        }
      }, error = function(e) {
        # Handle any errors during summary extraction
        tibble(term = NA, estimate = NA, std_error = NA, p_value = NA, 
               r_squared = NA, adj_r_squared = NA, AIC = NA,
               residual_std_error = NA, f_statistic = NA, model_p_value = NA)
      })

      return(summary_result)
    }, .id = "covariate") %>%
    mutate(functional_output = functional_output, pollutant = pollutant)  # Add separate columns for functional output and pollutant
  })

  return(model_summaries)
}
```

```{r}
# Run models
axys_func_mod_panc <- fit_all_models(axys_func_all_panc)
axys_func_mod_adip <- fit_all_models(axys_func_all_adip)

# Get metrics
axys_func_metrics_panc <- fit_models_metrics(axys_func_all_panc)
axys_func_metrics_adip <- fit_models_metrics(axys_func_all_adip)

# Get model summaries
axys_func_mod_panc_sum <- summarize_models(axys_func_mod_panc)
axys_func_mod_adip_sum <- summarize_models(axys_func_mod_adip)

write_csv(axys_func_mod_panc_sum, "2024-12-10_axys_func_log_mod_panc_summary.csv")
write_csv(axys_func_mod_adip_sum, "2024-12-10_axys_func_log_mod_adip_summary.csv")

# Filter for comparisons of specific functional output-pollutant pairs, if desired
# Example: Compare models for "high_glucose" output with "PCB1" pollutant
model_comparison <- model_metrics %>%
  filter(functional_outputs == "high_glucose", pollutants == "PCB1") %>%
  select(covariates, AIC, adj_r_squared)
```

```{r}
# Filter desired comparisons
model_comparisons_panc <- axys_main_corr %>%
  dplyr::filter(Tissue == "Pancreas", !Comparison %in% c("Age", "BMI", "Hba1c")) %>%
  left_join(axys_func_mod_panc_sum, by = c("Pollutant" = "pollutant", "Comparison" = "functional_output"))

model_comparisons_adip <- axys_main_corr %>%
  dplyr::filter(Tissue == "Adipose", !Comparison %in% c("Age", "BMI", "Hba1c")) %>%
  left_join(axys_func_mod_adip_sum, by = c("Pollutant" = "pollutant", "Comparison" = "functional_output"))

# write_csv(model_comparisons_panc, "2024-10-11_axys_func_log_mod_panc_filtered.csv")
# write_csv(model_comparisons_adip, "2024-10-11_axys_func_log_mod_adip_filtered.csv")

```

