---
title: "Correlating AXYS pollutant data with GSIS parameters"
author: "Angela Ching"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: yes
---

# Packages

```{r packages}
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)      # for data cleaning
library(scico)        # colour palettes
library(ggsci)        # colour palettes
library(ggpubr)       # for scatterplot correlations
library(psychometric) # masks "select" from dplyr; for CIr()
library(purrr)        # for mapping heatmaps
library(reshape2)     # for reshaping data for heatmaps
library(knitr)
library(pheatmap)
library(corrplot)
library(psych)
library(lme4)
```

# Notes from MH

IsletCore GSIS:
- Condition #1 = LG 2.8mM, HG 16.7mM 
- Condition #2 = LG 1mM, HG 16.7mM
- Condition #3 = LG 1mM, HG 10mM

Perifusion:
- Exclude KCl for donors: R361, R362, R385, R391 (already removed from final excel)
- Only use basal LG (exclude the rest of perifusion curve) for donors: R419, R421 (already removed from final excel)
- Do sensitivity analysis with donor R417

Exclusion criteria
- Remove any analyte with >50% donors below LOD
- Remove any analyte with >40% of donors with NDR flag

```{r}
# Get today's date for saving plots
date_today <- Sys.Date()
```

# Custom functions

```{r correlation_tests}
# Correlation tests

cor.mtest <- function(df, method = "kendall", ...) {
    n <- ncol(df)
    mat <- as.matrix(df[, 2:n])
    cor <- psych::corTest(mat, method = method, adjust = "fdr", use = "pairwise")
    cormat <- as.matrix(cor$r)
    pmat <- as.matrix(cor$p)
    return(list(cormat, pmat, cor))
}

# Flatten correlation matrix
cor.flat <- function(df, method = "kendall", ...) {
  n <- ncol(df)
  mat <- as.matrix(df[, 2:n])
  cor <- psych::corTest(mat, method = method, adjust = "fdr", use = "pairwise")
    
  # Convert p matrix to a data frame
  p_df <- as.data.frame(cor$p)
  p_df$row <- rownames(p_df)
  
  # Convert r matrix to a data frame
  r_df <- as.data.frame(cor$r)
  r_df$row <- rownames(r_df)
  
  # Melt the p matrix
  melted_p <- melt(p_df, id.vars = c("row"), variable.name = "column", value.name = "p")
  
  # Melt the r matrix
  melted_r <- melt(r_df, id.vars = c("row"), variable.name = "column", value.name = "r")
  
  # Combine the melted p and r data frames
  final_data <- left_join(melted_r, melted_p, by = c("row", "column")) %>%
  distinct(row, column, .keep_all = TRUE) %>%
  mutate(p_adj = p.adjust(.$p, method = "fdr"))
  
  return(final_data)
}

# Correlation matrix for plotting in Prism
cor.flat.for.mh <- function(df, method = "kendall", ...) {
  n <- ncol(df)
  mat <- as.matrix(df[, 2:n])
  cor_result <- psych::corTest(mat, method = method, use = "pairwise")
  
  # Extract Kendall's r values
  r_values <- cor_result$r
  
  # Keep only the upper triangle and diagonal elements
  upper_triangle <- upper.tri(r_values, diag = TRUE)
  r_values[!upper_triangle] <- NA
  
  # Convert r matrix to a data frame
  r_df <- as.data.frame(r_values)
  
  return(r_df)
}
```

```{r}
# Colour palettes
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
custom_palette <- c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA")

# Plot correlation
plot_correlation <- function(corrplot_data, index) {
  corrplot(corrplot_data[[1]], type = "upper", order = "original", method = "circle", cl.align.text = "l", diag = FALSE,
           addCoef.col = 'grey20', sig.level = 1, insig = 'blank',
           number.cex = 0.5, p.mat = corrplot_data[[2]], tl.col = "black", tl.srt = 45, tl.cex = 0.75)
}

# Generate and save correlation plots with flexible parameters
generate_and_save_corrplot <- function(filename, corrplot_data, width, height, show_legend = TRUE) {
  png(filename = filename, width = width, height = height, units = "in", res = 600)
  
  # Conditional cl.pos based on show_legend argument
  legend_position <- ifelse(show_legend, "l", "n")
  
  corrplot(corrplot_data[[1]], type = "upper", order = "original", method = "circle", 
           cl.align.text = legend_position, diag = FALSE, 
           addCoef.col = 'gray20', sig.level = 1, insig = 'blank', col = col(10),
           number.cex = 0.5, p.mat = corrplot_data[[2]], tl.col = "black", tl.srt = 45, tl.cex = 0.75,
           cl.pos = legend_position)
  
  dev.off()
}
```

```{r}
# Function for making correlation tables (x axis titles at a 45 degree angle)
plot_table <- function(data) {
  ggplot(data, aes(row, column, fill = r)) +
    geom_tile() +
    theme_minimal() +
    scale_fill_gradientn(colors = custom_palette, limits = c(-1, 1)) +
    # Additional scale_fill functions can be added here if needed
    theme(panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.spacing.y = unit(0.5, 'cm'),
          legend.title = element_text(size = 10),
          axis.text.x = element_text(size = 10, hjust = 1, angle = 45,  vjust = 1),
          axis.text.y = element_text(size = 10)) +
    geom_text(aes(label = round(r, 2)), color = "black", size = 2.5) +
    labs(fill = str_wrap("Kendall's coefficient", width = 12))
}

# Tables for correlations with donor characteristics (horizontal x axis titles)
plot_table_meta <- function(data) {
  ggplot(data, aes(row, column, fill = r)) +
    geom_tile() +
    theme_minimal() +
    scale_fill_gradientn(colors = custom_palette, limits = c(-1, 1)) +
    theme(panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.spacing.y = unit(0.5, 'cm'),
          legend.title = element_text(size = 10),
          axis.text.x = element_text(size = 10, hjust = 0.5, angle = 0,  vjust = 1),
          axis.text.y = element_text(size = 10)) +
    geom_text(aes(label = round(r, 2)), color = "black", size = 2.5) +
    labs(fill = str_wrap("Kendall's coefficient", width = 12))
}
```

```{r}
# Functions for performing Kendall correlations and filtering rows and columns by lab or data type
cor.mh <- function(df) {
  df %>%
    cor.flat() %>%
    dplyr::filter(!str_detect(row, "MH"), str_detect(column, "MH"))
}

cor.jk <- function(df) {
  df %>%
    cor.flat() %>%
    dplyr::filter(!str_detect(row, "JK"), str_detect(column, "JK"))
}

cor.adi <- function(df) {
  df %>%
    cor.flat() %>%
    dplyr::filter(!str_detect(row, "IsletCore"), str_detect(column, "IsletCore"))
}

cor.meta <- function(df) {
  df %>%
    cor.flat() %>%
    dplyr::filter((row == "Age" | row == "BMI" | row == "Hba1c") &
         !(column == "Age" | column == "BMI" | column == "Hba1c"))
}
```

```{r}
combine_correlations <- function(initial_corr, new_corr) {
  # Left join the two correlation tables based on 'row' and 'column'
  combined_corr <- dplyr::left_join(initial_corr, new_corr, by = c("row", "column"), suffix = c("_initial", "_new"))
  
  # Calculate the absolute percent change in r and add it as a new column
  combined_corr <- combined_corr %>%
    mutate(r_difference = round(abs(r_new - r_initial), 2),
           percent_change_r = round(abs((r_new - r_initial) / r_initial) * 100, 2),
           percent_change_r_dir = round((r_new - r_initial) / abs(r_initial) * 100, 2))
  
  return(combined_corr)
}
```

```{r}
# Save correlation matrices for export to prism
save_correlation_matrices <- function(correlation_list, date_today) {
  # Iterate over the outer list with imap
  imap(correlation_list, ~ {
    # Iterate over each sublist with imap
    imap(.x, ~ {
      # Create the file name for each element in the sublist
      file_name <- paste0(date_today, "_", .y, "_", .y, ".csv")
      # Write the CSV file
      write.csv(x = .x, file = file_name, row.names = TRUE)
    })
  })
}
```


# Load AXYS data

```{r AXYS_data}
# load chemical list
chem_list <- read_csv("../../data/2022-10-18_AXYS_chemicals_list_AC.csv") %>%
  dplyr::select(Compound, Dioxin_subtype)

chem_list_2 <- read_csv("../../data/2024-10-01_AXYS_chemicals_list_with_coelutions.csv") %>%
  dplyr::select(-c(Dioxin_subtype, Type))

# load AXYS data
axys_pops <- read_csv("../../outputs/2024-08-24_ProjectGrant_excluded_outliers_for_single_analyte_analyses.csv") %>%
  dplyr::select(-c(CONC_BLANK_adj, IS_BLANK_ADJ_CONC_HIGHER_THAN_LOD)) %>%
  mutate(BLANK_and_LOD_adj = as.numeric(BLANK_and_LOD_adj),
         File = factor(File),
         COMPOUND = case_when(str_detect(COMPOUND, "TOTAL") ~ str_to_sentence(COMPOUND),
                              str_detect(COMPOUND, " Epoxide") ~ str_to_sentence(COMPOUND),
                              TRUE ~ COMPOUND),
         across(where(is.character), str_squish))

axys_pops_2 <- axys_pops %>%
  dplyr::select(-c(File, LAB_FLAG, DETECTION_LIMIT)) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS data with imputed values for true NAs (chemicals not measured by AXYS in certain donors)
axys_pops_imputed_panc <- read_excel("../../outputs/2024-09-03_axys_pops_includes_imputed_values_for_true_NAs_using_mice_package.xlsx", sheet = 1)

axys_pops_imputed_adip <- read_excel("../../outputs/2024-09-03_axys_pops_includes_imputed_values_for_true_NAs_using_mice_package.xlsx", sheet = 2)

# load AXYS donor metadata
axys_metadata <- read_csv("../../data/2024-08-22_donor_characteristics_FINAL.csv", show_col_types = FALSE) %>%
  mutate(BMI_category = case_when(BMI < 24.9 ~ "Lean",
                                  BMI >= 24.9 & BMI <= 29.9 ~ "Overweight",
                                  BMI > 29.9 ~ "Obese"),
         Hba1c_category = case_when(Hba1c < 6 ~ "Normoglycemic",
                                    Hba1c <= 6.5 ~ "Prediabetic",
                                    Hba1c > 6.5 ~ "Diabetic"),
         BMI_category = factor(BMI_category, levels = c("Lean", "Overweight", "Obese")),
         Hba1c_category = factor(Hba1c_category, levels = c("Normoglycemic", "Prediabetic", "Diabetic")),
         Sex = as_factor(Sex),
         Diabetes_status = as_factor(Diabetes_status)) %>%
  dplyr::select(-Purity)

# Donor IDs
axys_donors <- axys_metadata %>%
  dplyr::select(Id)

# Subset data by tissue type
subset_tissue <- function(tissue) {
  axys_pops_2 %>%
    dplyr::filter(!str_detect(COMPOUND, "Total"), TISSUE_TYPE == tissue) %>%
    dplyr::select(DONOR, COMPOUND, BLANK_and_LOD_adj) %>%
    group_by(DONOR) %>%
    pivot_wider(names_from = COMPOUND, values_from = BLANK_and_LOD_adj) %>%
    ungroup()
}

axys_pops_panc <- subset_tissue("Pancreas")
axys_pops_adip <- subset_tissue("Adipose")
```

```{r}
# Create compounds list
dioxin_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin") %>%
  dplyr::pull(Compound)

pcb_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin-like" | Dioxin_similarity == "Non-dioxin-like") %>%
  dplyr::pull(Compound)

ocp_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "OCP") %>%
  dplyr::pull(Compound)
```

```{r}
# Calculate sums
axys_panc_sums <- axys_pops_panc %>%
  pivot_longer(cols = c(2:34), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("Dioxin-like", "Non-dioxin-like")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

axys_adip_sums <- axys_pops_adip %>%
  pivot_longer(cols = c(2:42), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("Dioxin-like", "Non-dioxin-like")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

axys_pops_imputed_panc_sums <- axys_pops_imputed_panc %>%
  pivot_longer(cols = c(2:34), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("Dioxin-like", "Non-dioxin-like")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

axys_pops_imputed_adip_sums <- axys_pops_imputed_adip %>%
  pivot_longer(cols = c(2:42), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("Dioxin-like", "Non-dioxin-like")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()
```

```{r}
# Combine single analyte concentrations with sums
axys_pops_with_sums_panc <- axys_pops_panc %>%
  left_join(., axys_panc_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip <- axys_pops_adip %>%
  left_join(., axys_adip_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_panc_imp <- axys_pops_imputed_panc %>%
  left_join(., axys_pops_imputed_panc_sums, by = c("DONOR" = "DONOR"))
  
axys_pops_with_sums_adip_imp <- axys_pops_imputed_adip %>%
  left_join(., axys_pops_imputed_adip_sums, by = c("DONOR" = "DONOR"))
```

```{r}
# Combine analyte concentrations with metadata
axys_pops_with_sums_panc_meta <- axys_pops_with_sums_panc %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta <- axys_pops_with_sums_adip %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_panc_meta_imp <- axys_pops_with_sums_panc_imp %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta_imp <- axys_pops_with_sums_adip_imp %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)
```

# Sensitivity analyses

```{r}
# Remove outlier donors
rm_ind_adip <- c("R419", "R421")
rm_ind_panc <- c("R389", "R419", "R448")
```

```{r}
## Dioxins

# Pancreas
axys_pops_panc_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_dioxin_imp <- axys_pops_with_sums_panc_imp %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_ind_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_389_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_419_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_448_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

# Adipose
axys_pops_adip_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_dioxin_imp <- axys_pops_with_sums_adip_imp %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_rm_ind_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_rm_419_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_rm_421_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)
```

```{r}
## PCBs

#Pancreas
axys_pops_panc_pcb <- axys_pops_with_sums_panc %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_panc_pcb_imp <- axys_pops_with_sums_panc_imp %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_panc_rm_ind_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_panc_rm_389_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_panc_rm_419_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_panc_rm_448_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

# Adipose
axys_pops_adip_pcb <- axys_pops_with_sums_adip %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_adip_pcb_imp <- axys_pops_with_sums_adip_imp %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_adip_rm_ind_pcb <- axys_pops_with_sums_adip %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_adip_rm_419_pcb <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")

axys_pops_adip_rm_421_pcb <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "Dioxin-like", "Non-dioxin-like")
```

```{r}
## OCPs

# Pancreas
axys_pops_panc_ocp <- axys_pops_with_sums_panc %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_ocp_imp <- axys_pops_with_sums_panc_imp %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_ind_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_389_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_419_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_448_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(ocp_list))

# Adipose
axys_pops_adip_ocp <- axys_pops_with_sums_adip %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_ocp_imp <- axys_pops_with_sums_adip_imp %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_rm_ind_ocp <- axys_pops_with_sums_adip %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_rm_419_ocp <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_rm_421_ocp <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(ocp_list))
```

## Correlate concentrations of each analyte with each other within each tissue

```{r}
# Create a list of correlation matrices and their corresponding p-values: Kendall
axys_analytes_list_panc <- list(
  axys_pops_panc_dioxin = axys_pops_panc_dioxin,
  axys_pops_panc_pcb = axys_pops_panc_pcb,
  axys_pops_panc_ocp = axys_pops_panc_ocp
)

axys_analytes_list_panc_imp <- list(
  axys_pops_panc_dioxin_imp = axys_pops_panc_dioxin_imp,
  axys_pops_panc_pcb_imp = axys_pops_panc_pcb_imp,
  axys_pops_panc_ocp_imp = axys_pops_panc_ocp_imp
)

axys_analytes_list_panc_rm_ind <- list(
  axys_pops_panc_rm_ind_dioxin = axys_pops_panc_rm_ind_dioxin,
  axys_pops_panc_rm_ind_pcb = axys_pops_panc_rm_ind_pcb,
  axys_pops_panc_rm_ind_ocp = axys_pops_panc_rm_ind_ocp
)

axys_analytes_list_panc_rm_389 <- list(
  axys_pops_panc_rm_389_dioxin = axys_pops_panc_rm_389_dioxin,
  axys_pops_panc_rm_389_pcb = axys_pops_panc_rm_389_pcb,
  axys_pops_panc_rm_389_ocp = axys_pops_panc_rm_389_ocp
)

axys_analytes_list_panc_rm_419 <- list(
  axys_pops_panc_rm_419_dioxin = axys_pops_panc_rm_419_dioxin,
  axys_pops_panc_rm_419_pcb = axys_pops_panc_rm_419_pcb,
  axys_pops_panc_rm_419_ocp = axys_pops_panc_rm_419_ocp
)

axys_analytes_list_panc_rm_448 <- list(
  axys_pops_panc_rm_448_dioxin = axys_pops_panc_rm_448_dioxin,
  axys_pops_panc_rm_448_pcb = axys_pops_panc_rm_448_pcb,
  axys_pops_panc_rm_448_ocp = axys_pops_panc_rm_448_ocp
)

axys_analytes_list_adip <- list(
  axys_pops_adip_dioxin = axys_pops_adip_dioxin,
  axys_pops_adip_pcb = axys_pops_adip_pcb,
  axys_pops_adip_ocp = axys_pops_adip_ocp
)

axys_analytes_list_adip_imp <- list(
  axys_pops_adip_dioxin_imp = axys_pops_adip_dioxin_imp,
  axys_pops_adip_pcb_imp = axys_pops_adip_pcb_imp,
  axys_pops_adip_ocp_imp = axys_pops_adip_ocp_imp
)

axys_analytes_list_adip_rm_ind <- list(
  axys_pops_adip_rm_ind_dioxin = axys_pops_adip_rm_ind_dioxin,
  axys_pops_adip_rm_ind_pcb = axys_pops_adip_rm_ind_pcb,
  axys_pops_adip_rm_ind_ocp = axys_pops_adip_rm_ind_ocp
)

axys_analytes_list_adip_rm_419 <- list(
  axys_pops_adip_rm_419_dioxin = axys_pops_adip_rm_419_dioxin,
  axys_pops_adip_rm_419_pcb = axys_pops_adip_rm_419_pcb,
  axys_pops_adip_rm_419_ocp = axys_pops_adip_rm_419_ocp
)

axys_analytes_list_adip_rm_421 <- list(
  axys_pops_adip_rm_421_dioxin = axys_pops_adip_rm_421_dioxin,
  axys_pops_adip_rm_421_pcb = axys_pops_adip_rm_421_pcb,
  axys_pops_adip_rm_421_ocp = axys_pops_adip_rm_421_ocp
) 
```

```{r, fig.width = 8}
# Perform kendall correlations
corr_axys_analytes_panc <- map(axys_analytes_list_panc, cor.mtest)
corr_axys_analytes_panc_imp <- map(axys_analytes_list_panc_imp, cor.mtest)
corr_axys_analytes_panc_rm_ind <- map(axys_analytes_list_panc_rm_ind, cor.mtest)
corr_axys_analytes_panc_rm_389 <- map(axys_analytes_list_panc_rm_389, cor.mtest)
corr_axys_analytes_panc_rm_419 <- map(axys_analytes_list_panc_rm_419, cor.mtest)
corr_axys_analytes_panc_rm_448 <- map(axys_analytes_list_panc_rm_448, cor.mtest)

corr_axys_analytes_adip <- map(axys_analytes_list_adip, cor.mtest)
corr_axys_analytes_adip_imp <- map(axys_analytes_list_adip_imp, cor.mtest)
corr_axys_analytes_adip_rm_ind <- map(axys_analytes_list_adip_rm_ind, cor.mtest)
corr_axys_analytes_adip_rm_419 <- map(axys_analytes_list_adip_rm_419, cor.mtest)
corr_axys_analytes_adip_rm_421 <- map(axys_analytes_list_adip_rm_421, cor.mtest)

# Map the plotting function over the list of correlation matrices
imap(corr_axys_analytes_panc, plot_correlation)
imap(corr_axys_analytes_panc_imp, plot_correlation)
imap(corr_axys_analytes_panc_rm_ind, plot_correlation)
imap(corr_axys_analytes_panc_rm_389, plot_correlation)
imap(corr_axys_analytes_panc_rm_419, plot_correlation)
imap(corr_axys_analytes_panc_rm_448, plot_correlation)

imap(corr_axys_analytes_adip, plot_correlation)
imap(corr_axys_analytes_adip_imp, plot_correlation)
imap(corr_axys_analytes_adip_rm_ind, plot_correlation)
imap(corr_axys_analytes_adip_rm_419, plot_correlation)
imap(corr_axys_analytes_adip_rm_421, plot_correlation)

# Generate and export plots
# generate_and_save_corrplot("2024-02-27_ProjectGrant_pancreas_pcb_unadjusted_p_0.05_kendall.png", axys_panc_pcb_corr_k, width = 6, height = 6)
```

```{r}
# Perform kendall correlations and export to csv for MH
corr_axys_analytes_panc_csv <- map(axys_analytes_list_panc, cor.flat.for.mh)
corr_axys_analytes_panc_imp_csv <- map(axys_analytes_list_panc_imp, cor.flat.for.mh)
corr_axys_analytes_panc_rm_ind_csv <- map(axys_analytes_list_panc_rm_ind, cor.flat.for.mh)
corr_axys_analytes_panc_rm_389_csv <- map(axys_analytes_list_panc_rm_389, cor.flat.for.mh)
corr_axys_analytes_panc_rm_419_csv <- map(axys_analytes_list_panc_rm_419, cor.flat.for.mh)
corr_axys_analytes_panc_rm_448_csv <- map(axys_analytes_list_panc_rm_448, cor.flat.for.mh)

corr_axys_analytes_adip_csv <- map(axys_analytes_list_adip, cor.flat.for.mh)
corr_axys_analytes_adip_imp_csv <- map(axys_analytes_list_adip_imp, cor.flat.for.mh)
corr_axys_analytes_adip_rm_ind_csv <- map(axys_analytes_list_adip_rm_ind, cor.flat.for.mh)
corr_axys_analytes_adip_rm_419_csv <- map(axys_analytes_list_adip_rm_419, cor.flat.for.mh)
corr_axys_analytes_adip_rm_421_csv <- map(axys_analytes_list_adip_rm_421, cor.flat.for.mh)

# map2(corr_axys_analytes_k_csv, names(corr_axys_analytes_k_csv), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, ".csv"), row.names = TRUE)
# })

corr_axys_analytes_csv <- list(
  corr_axys_analytes_panc_csv,
  corr_axys_analytes_panc_imp_csv,
  corr_axys_analytes_panc_rm_ind_csv,
  corr_axys_analytes_panc_rm_389_csv,
  corr_axys_analytes_panc_rm_419_csv,
  corr_axys_analytes_panc_rm_448_csv,
  
  corr_axys_analytes_adip_csv,
  corr_axys_analytes_adip_imp_csv,
  corr_axys_analytes_adip_rm_ind_csv,
  corr_axys_analytes_adip_rm_419_csv,
  corr_axys_analytes_adip_rm_421_csv
)

# save_correlation_matrices(corr_axys_analytes_csv, date_today = Sys.Date())
```

## Calculate percent change in correlation coefficient

```{r}
# Extract table for percent change in correlation coefficient
corr_axys_panc_analytes_orig_tbl <- map(axys_analytes_list_panc, cor.flat)
corr_axys_panc_analytes_imputed_tbl <- map(axys_analytes_list_panc_imp, cor.flat)
corr_axys_panc_analytes_rm_outliers_tbl <- map(axys_analytes_list_panc_rm_ind, cor.flat)
corr_axys_panc_analytes_rm_389_tbl <- map(axys_analytes_list_panc_rm_389, cor.flat)
corr_axys_panc_analytes_rm_419_tbl <- map(axys_analytes_list_panc_rm_419, cor.flat)
corr_axys_panc_analytes_rm_448_tbl <- map(axys_analytes_list_panc_rm_448, cor.flat)

corr_axys_adip_analytes_orig_tbl <- map(axys_analytes_list_adip, cor.flat)
corr_axys_adip_analytes_imputed_tbl <- map(axys_analytes_list_adip_imp, cor.flat)
corr_axys_adip_analytes_rm_outliers_tbl <- map(axys_analytes_list_adip_rm_ind, cor.flat)
corr_axys_adip_analytes_rm_419_tbl <- map(axys_analytes_list_adip_rm_419, cor.flat)
corr_axys_adip_analytes_rm_421_tbl <- map(axys_analytes_list_adip_rm_421, cor.flat)
```

```{r}
# Combine correlations before and after removing outliers
corr_axys_panc_analytes_orig_vs_imputed <- map2(corr_axys_panc_analytes_orig_tbl, corr_axys_panc_analytes_imputed_tbl, combine_correlations)
corr_axys_panc_analytes_orig_vs_rm_outliers <- map2(corr_axys_panc_analytes_orig_tbl, corr_axys_panc_analytes_rm_outliers_tbl, combine_correlations)
corr_axys_panc_analytes_orig_vs_rm_389 <- map2(corr_axys_panc_analytes_orig_tbl, corr_axys_panc_analytes_rm_389_tbl, combine_correlations)
corr_axys_panc_analytes_orig_vs_rm_419 <- map2(corr_axys_panc_analytes_orig_tbl, corr_axys_panc_analytes_rm_419_tbl, combine_correlations)
corr_axys_panc_analytes_orig_vs_rm_448 <- map2(corr_axys_panc_analytes_orig_tbl, corr_axys_panc_analytes_rm_448_tbl, combine_correlations)

corr_axys_adip_analytes_orig_vs_imputed <- map2(corr_axys_adip_analytes_orig_tbl, corr_axys_adip_analytes_imputed_tbl, combine_correlations)
corr_axys_adip_analytes_orig_vs_rm_outliers <- map2(corr_axys_adip_analytes_orig_tbl, corr_axys_adip_analytes_rm_outliers_tbl, combine_correlations)
corr_axys_adip_analytes_orig_vs_rm_419 <- map2(corr_axys_adip_analytes_orig_tbl, corr_axys_adip_analytes_rm_419_tbl, combine_correlations)
corr_axys_adip_analytes_orig_vs_rm_421 <- map2(corr_axys_adip_analytes_orig_tbl, corr_axys_adip_analytes_rm_421_tbl, combine_correlations)
```

```{r}
# Create a list to export to csv

corr_axys_analytes_rchange_csv <- list(
  # Pancreas
  corr_axys_panc_analytes_orig_vs_imputed = corr_axys_panc_analytes_orig_vs_imputed,
  corr_axys_panc_analytes_orig_vs_rm_outliers = corr_axys_panc_analytes_orig_vs_rm_outliers,
  corr_axys_panc_analytes_orig_vs_rm_389 = corr_axys_panc_analytes_orig_vs_rm_389,
  corr_axys_panc_analytes_orig_vs_rm_419 = corr_axys_panc_analytes_orig_vs_rm_419,
  corr_axys_panc_analytes_orig_vs_rm_448 = corr_axys_panc_analytes_orig_vs_rm_448,
  
  # Adipose
  corr_axys_adip_analytes_orig_vs_imputed = corr_axys_adip_analytes_orig_vs_imputed,
  corr_axys_adip_analytes_orig_vs_rm_outliers = corr_axys_adip_analytes_orig_vs_rm_outliers,
  corr_axys_adip_analytes_orig_vs_rm_419 = corr_axys_adip_analytes_orig_vs_rm_419,
  corr_axys_adip_analytes_orig_vs_rm_421 = corr_axys_adip_analytes_orig_vs_rm_421
)

# Export to csv
# map2(corr_axys_panc_analytes_orig_vs_imputed, names(corr_axys_panc_analytes_orig_vs_imputed), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, "-change_in_analyte-to-analyte_corr_after_imputation", ".csv"), row.names = TRUE)
# })

# map2(corr_axys_panc_analytes_orig_vs_rm_outliers, names(corr_axys_panc_analytes_orig_vs_rm_outliers), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, "-change_in_analyte-to-analyte_corr_after_removing_outliers", ".csv"), row.names = TRUE)
# })

# map2(corr_axys_panc_analytes_orig_vs_rm_389, names(corr_axys_panc_analytes_orig_vs_rm_389), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, "-change_in_analyte-to-analyte_corr_after_removing_R389", ".csv"), row.names = TRUE)
# })
```

```{r}
# Generate and export tables as png
## Individual analytes
axys_meta_corr_table <- map(axys_meta_ken, plot_table_meta)
#map2(axys_meta_corr_table, names(axys_meta_corr_table), ~ ggsave(filename = paste0(date_today, "_", .y, ".png"), plot = .x, width = 5.5, height = 5.5, units = "in", dpi = 600, scale = 1))

## Sums
axys_meta_corr_table_sums <- map(axys_meta_ken_sums, plot_table_meta)
#map2(axys_meta_corr_table_sums, names(axys_meta_corr_table_sums), ~ ggsave(filename = paste0(date_today, "_", .y, ".png"), plot = .x, width = 5.5, height = 3.5, units = "in", dpi = 600, scale = 1))
```

# Load GSIS and perifusion data



## Combine POPs data with functional parameters

```{r}
## Pancreas

# Pancreas sums
mh_peri_panc_sums <- left_join(glu_peri_mh_t, axys_panc_sums, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421") %>%
  dplyr::select(-TISSUE_TYPE)

glu_peri_jk_panc_sums <- left_join(axys_panc_sums, glu_peri_jk_t, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

leu_peri_jk_panc_sums <- left_join(axys_panc_sums, leu_peri_jk_t, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

fa_peri_jk_panc_sums <- left_join(axys_panc_sums, fa_peri_jk_t, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

gsis_adi_panc_sums <- left_join(axys_panc_sums, gsis_adi, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

# Panreas dioxins
mh_peri_panc_dioxin <- left_join(glu_peri_mh_t, axys_panc_dioxin, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421")

glu_peri_jk_panc_dioxin <- left_join(axys_panc_dioxin, glu_peri_jk_t, by = c("DONOR" = "Donor")) 

leu_peri_jk_panc_dioxin <- left_join(axys_panc_dioxin, leu_peri_jk_t, by = c("DONOR" = "Donor"))

fa_peri_jk_panc_dioxin <- left_join(axys_panc_dioxin, fa_peri_jk_t, by = c("DONOR" = "Donor"))

gsis_adi_panc_dioxin <- left_join(axys_panc_dioxin, gsis_adi, by = c("DONOR" = "Donor"))

# Panreas PCBs
mh_peri_panc_pcb <- left_join(glu_peri_mh_t, axys_panc_pcb, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421")

glu_peri_jk_panc_pcb <- left_join(axys_panc_pcb, glu_peri_jk_t, by = c("DONOR" = "Donor")) 

leu_peri_jk_panc_pcb <- left_join(axys_panc_pcb, leu_peri_jk_t, by = c("DONOR" = "Donor"))

fa_peri_jk_panc_pcb <- left_join(axys_panc_pcb, fa_peri_jk_t, by = c("DONOR" = "Donor"))

gsis_adi_panc_pcb <- left_join(axys_panc_pcb, gsis_adi, by = c("DONOR" = "Donor"))

# Panreas OCPs
mh_peri_panc_ocp <- left_join(glu_peri_mh_t, axys_panc_ocp, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421")

glu_peri_jk_panc_ocp <- left_join(axys_panc_ocp, glu_peri_jk_t, by = c("DONOR" = "Donor")) 

leu_peri_jk_panc_ocp <- left_join(axys_panc_ocp, leu_peri_jk_t, by = c("DONOR" = "Donor"))

fa_peri_jk_panc_ocp <- left_join(axys_panc_ocp, fa_peri_jk_t, by = c("DONOR" = "Donor"))

gsis_adi_panc_ocp <- left_join(axys_panc_ocp, gsis_adi, by = c("DONOR" = "Donor"))
```

```{r}
## Adipose

# Adipose sums
mh_peri_adip_sums <- left_join(glu_peri_mh_t, axys_adip_sums, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421") %>%
  dplyr::select(-TISSUE_TYPE)

glu_peri_jk_adip_sums <- left_join(axys_adip_sums, glu_peri_jk_t, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

leu_peri_jk_adip_sums <- left_join(axys_adip_sums, leu_peri_jk_t, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

fa_peri_jk_adip_sums <- left_join(axys_adip_sums, fa_peri_jk_t, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

gsis_adi_adip_sums <- left_join(axys_adip_sums, gsis_adi, by = c("DONOR" = "Donor")) %>%
  dplyr::select(-TISSUE_TYPE)

# Adipose dioxins
mh_peri_adip_dioxin <- left_join(glu_peri_mh_t, axys_adip_dioxin, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421")

glu_peri_jk_adip_dioxin <- left_join(axys_adip_dioxin, glu_peri_jk_t, by = c("DONOR" = "Donor")) 

leu_peri_jk_adip_dioxin <- left_join(axys_adip_dioxin, leu_peri_jk_t, by = c("DONOR" = "Donor"))

fa_peri_jk_adip_dioxin <- left_join(axys_adip_dioxin, fa_peri_jk_t, by = c("DONOR" = "Donor"))

gsis_adi_adip_dioxin <- left_join(axys_adip_dioxin, gsis_adi, by = c("DONOR" = "Donor"))

# Adipose PCBs
mh_peri_adip_pcb <- left_join(glu_peri_mh_t, axys_adip_pcb, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421")

glu_peri_jk_adip_pcb <- left_join(axys_adip_pcb, glu_peri_jk_t, by = c("DONOR" = "Donor")) 

leu_peri_jk_adip_pcb <- left_join(axys_adip_pcb, leu_peri_jk_t, by = c("DONOR" = "Donor"))

fa_peri_jk_adip_pcb <- left_join(axys_adip_pcb, fa_peri_jk_t, by = c("DONOR" = "Donor"))

gsis_adi_adip_pcb <- left_join(axys_adip_pcb, gsis_adi, by = c("DONOR" = "Donor"))

# Adipose OCPs
mh_peri_adip_ocp <- left_join(glu_peri_mh_t, axys_adip_ocp, by = c("Donor" = "DONOR")) %>%
  dplyr::filter(Donor != "R419", Donor != "R421")

glu_peri_jk_adip_ocp <- left_join(axys_adip_ocp, glu_peri_jk_t, by = c("DONOR" = "Donor")) 

leu_peri_jk_adip_ocp <- left_join(axys_adip_ocp, leu_peri_jk_t, by = c("DONOR" = "Donor"))

fa_peri_jk_adip_ocp <- left_join(axys_adip_ocp, fa_peri_jk_t, by = c("DONOR" = "Donor"))

gsis_adi_adip_ocp <- left_join(axys_adip_ocp, gsis_adi, by = c("DONOR" = "Donor"))
```


## Correlate POPs vs functional parameters

```{r}
# Create correlation lists
corr_list_mh <- list(
  mh_peri_panc_sums = mh_peri_panc_sums, # Pancreas sums
  mh_peri_panc_dioxin = mh_peri_panc_dioxin, # Panreas dioxins
  mh_peri_panc_pcb = mh_peri_panc_pcb, # Panreas PCBs
  mh_peri_panc_ocp =  mh_peri_panc_ocp, # Panreas OCPs
  
  mh_peri_adip_sums =  mh_peri_adip_sums, # Adipose sums
  mh_peri_adip_dioxin = mh_peri_adip_dioxin, # Adipose dioxins
  mh_peri_adip_pcb = mh_peri_adip_pcb, # Adipose PCBs
  mh_peri_adip_ocp = mh_peri_adip_ocp # Adipose OCPs
)

corr_list_adi <- list(
  gsis_adi_panc_sums = gsis_adi_panc_sums, # Pancreas sums
  gsis_adi_panc_dioxin = gsis_adi_panc_dioxin, # Panreas dioxins
  gsis_adi_panc_pcb = gsis_adi_panc_pcb, # Panreas PCBs
  gsis_adi_panc_ocp = gsis_adi_panc_ocp, # Panreas OCPs
  
  gsis_adi_adip_sums = gsis_adi_adip_sums, # Adipose sums
  gsis_adi_adip_dioxin = gsis_adi_adip_dioxin, # Adipose dioxins
  gsis_adi_adip_pcb = gsis_adi_adip_pcb, # Adipose PCBs
  gsis_adi_adip_ocp = gsis_adi_adip_ocp # Adipose OCPs
)

corr_list_jk <- list(
  # Pancreas sums
  glu_peri_jk_panc_sums = glu_peri_jk_panc_sums,
  leu_peri_jk_panc_sums = leu_peri_jk_panc_sums,
  fa_peri_jk_panc_sums = fa_peri_jk_panc_sums,
  
  # Panreas dioxins
  glu_peri_jk_panc_dioxin = glu_peri_jk_panc_dioxin,
  leu_peri_jk_panc_dioxin = leu_peri_jk_panc_dioxin,
  fa_peri_jk_panc_dioxin = fa_peri_jk_panc_dioxin,
  
  # Panreas PCBs
  glu_peri_jk_panc_pcb = glu_peri_jk_panc_pcb,
  leu_peri_jk_panc_pcb = leu_peri_jk_panc_pcb,
  fa_peri_jk_panc_pcb = fa_peri_jk_panc_pcb,
  
  # Panreas OCPs
  glu_peri_jk_panc_ocp = glu_peri_jk_panc_ocp,
  leu_peri_jk_panc_ocp = leu_peri_jk_panc_ocp,
  fa_peri_jk_panc_ocp = fa_peri_jk_panc_ocp,
  
  # Adipose sums
  glu_peri_jk_adip_sums = glu_peri_jk_adip_sums,
  leu_peri_jk_adip_sums = leu_peri_jk_adip_sums,
  fa_peri_jk_adip_sums = fa_peri_jk_adip_sums,
  
  # Adipose dioxins
  glu_peri_jk_adip_dioxin = glu_peri_jk_adip_dioxin, 
  leu_peri_jk_adip_dioxin = leu_peri_jk_adip_dioxin, 
  fa_peri_jk_adip_dioxin = fa_peri_jk_adip_dioxin, 
  
  # Adipose PCBs
  glu_peri_jk_adip_pcb = glu_peri_jk_adip_pcb, 
  leu_peri_jk_adip_pcb = leu_peri_jk_adip_pcb, 
  fa_peri_jk_adip_pcb = fa_peri_jk_adip_pcb, 
  
  # Adipose OCPs
  glu_peri_jk_adip_ocp = glu_peri_jk_adip_ocp, 
  leu_peri_jk_adip_ocp = leu_peri_jk_adip_ocp, 
  fa_peri_jk_adip_ocp = fa_peri_jk_adip_ocp
)
```

```{r, fig.width = 9}
# Perform correlations and export tables as png files
corr_ken_mh <- map(corr_list_mh, cor.mh)
corr_ken_mh_plots <- map(corr_ken_mh, plot_table)
#map2(corr_ken_mh_plots, names(corr_ken_mh_plots), ~ ggsave(filename = paste0(date_today, "_", .y, ".png"), plot = .x, width = 8, height = 6, units = "in", dpi = 600, scale = 1))

corr_ken_jk <- map(corr_list_jk, cor.jk)
corr_ken_jk_plots <- map(corr_ken_jk, plot_table)
#map2(corr_ken_jk_plots, names(corr_ken_jk_plots), ~ ggsave(filename = paste0(date_today, "_", .y, ".png"), plot = .x, width = 8, height = 6, units = "in", dpi = 600, scale = 1))

corr_ken_adi <- map(corr_list_adi, cor.adi)
corr_ken_adi_plots <- map(corr_ken_adi, plot_table)
#map2(corr_ken_adi_plots, names(corr_ken_adi_plots), ~ ggsave(filename = paste0(date_today, "_", .y, ".png"), plot = .x, width = 8, height = 6, units = "in", dpi = 600, scale = 1))
```

```{r}
# Perform kendall correlations and export to csv for MH
corr_ken_mh_csv <- map(corr_list_mh, cor.flat.for.mh)
# map2(corr_ken_mh_csv, names(corr_ken_mh_csv), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, ".csv"), row.names = TRUE)
# })

corr_ken_jk_csv <- map(corr_list_jk, cor.flat.for.mh)
# map2(corr_ken_jk_csv, names(corr_ken_jk_csv), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, ".csv"), row.names = TRUE)
# })

corr_ken_adi_csv <- map(corr_list_adi, cor.flat.for.mh)
# map2(corr_ken_adi_csv, names(corr_ken_adi_csv), ~ {
#   write.csv(x = .x, file = paste0(date_today, "_", .y, ".csv"), row.names = TRUE)
# })
```

# Session Info

```{r}
sessionInfo()
```

