---
title: "Correlating AXYS pollutant concentrations within each tissue and with GSIS parameters for each tissue"
author: "Angela Ching"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: yes
---

# Notes from MH

IsletCore GSIS:
- Condition #1 = LG 2.8mM, HG 16.7mM 
- Condition #2 = LG 1mM, HG 16.7mM
- Condition #3 = LG 1mM, HG 10mM

Perifusion:
- Exclude KCl for donors: R361, R362, R385, R391 (already removed from final excel)
- Only use basal LG (exclude the rest of perifusion curve) for donors: R419, R421 (already removed from final excel)

Exclusion criteria
- Remove any analyte with >50% donors below LOD
- Remove any analyte with >40% of donors with NDR flag

# Packages

```{r packages}
library(tidyverse)    # contains ggplot2, purrr, etc.
library(readxl)
library(janitor)      # for data cleaning
library(scico)        # colour palettes
library(ggsci)        # colour palettes
library(ggpubr)       # for scatterplot correlations
library(psychometric) # masks "select" from dplyr; for CIr()
library(reshape2)     # for reshaping data for heatmaps
library(knitr)
library(pheatmap)
library(corrplot)
library(psych)
library(lme4)
library(here)
```

# Load necessary functions

```{r}
source(here::here("functions", "correlation_functions.R"))  # General correlation functions
source(here::here("functions", "correlations_gsis.R"))      # Correlate analyte concentrations with different GSIS parameters
source(here::here("functions", "plotting_functions.R"))     # Plotting functions
source(here::here("functions", "percent_change.R"))         # Calculate percent change (sensitivity analyses)
```

# Load AXYS data

```{r}
# load chemical list
chem_list <- read_csv(here::here("data", "2022-10-18_AXYS_chemicals_list_AC.csv")) %>%
  dplyr::select(Compound, Dioxin_subtype) %>%
  mutate(across(where(is.character), str_squish))

chem_list_2 <- read_csv(here::here("data", "2024-10-01_AXYS_chemicals_list_with_coelutions.csv")) %>%
  dplyr::select(-c(Dioxin_subtype, Type)) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS data
axys_pops <- read_csv(here::here("outputs", "2024-08-24_ProjectGrant_excluded_outliers_for_single_analyte_analyses.csv")) %>%
  dplyr::select(-c(CONC_BLANK_adj, IS_BLANK_ADJ_CONC_HIGHER_THAN_LOD)) %>%
  mutate(BLANK_and_LOD_adj = as.numeric(BLANK_and_LOD_adj),
         File = factor(File),
         COMPOUND = case_when(str_detect(COMPOUND, "TOTAL") ~ str_to_sentence(COMPOUND),
                              str_detect(COMPOUND, " Epoxide") ~ str_to_sentence(COMPOUND),
                              TRUE ~ COMPOUND),
         across(where(is.character), str_squish))

axys_pops_2 <- axys_pops %>%
  dplyr::select(-c(File, LAB_FLAG, DETECTION_LIMIT)) %>%
  mutate(across(where(is.character), str_squish))

# load adipose-to-pancreas ratios
adip_panc <- read_csv(here::here("data", "2025-08-06_adipose-to-pancreas_ratio.csv")) %>%
  mutate(COMPOUND = case_when(str_detect(COMPOUND, " Epoxide") ~ str_to_sentence(COMPOUND),
                                     TRUE ~ COMPOUND),
                across(where(is.character), str_squish))

# load AXYS data with imputed values for true NAs (chemicals not measured by AXYS in certain donors)
axys_pops_imputed_panc <- read_excel(here::here("outputs", "2024-09-03_axys_pops_includes_imputed_values_for_true_NAs_using_mice_package.xlsx"), sheet = 1) %>%
  mutate(across(where(is.character), str_squish))

axys_pops_imputed_adip <- read_excel(here::here("outputs", "2024-09-03_axys_pops_includes_imputed_values_for_true_NAs_using_mice_package.xlsx"), sheet = 2) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS donor metadata
axys_metadata <- read_csv(here::here("data", "2024-08-22_donor_characteristics_FINAL.csv"), show_col_types = FALSE) %>%
  mutate(BMI_category = case_when(BMI < 24.9 ~ "Lean",
                                  BMI >= 24.9 & BMI <= 29.9 ~ "Overweight",
                                  BMI > 29.9 ~ "Obese"),
         Hba1c_category = case_when(Hba1c < 6 ~ "Normoglycemic",
                                    Hba1c <= 6.5 ~ "Prediabetic",
                                    Hba1c > 6.5 ~ "Diabetic"),
         BMI_category = factor(BMI_category, levels = c("Lean", "Overweight", "Obese")),
         Hba1c_category = factor(Hba1c_category, levels = c("Normoglycemic", "Prediabetic", "Diabetic")),
         Sex = as_factor(Sex),
         Diabetes_status = as_factor(Diabetes_status)) %>%
  dplyr::select(-Purity)

# Subset data by sex
axys_females <- axys_metadata %>%
  dplyr::filter(Sex == "F") %>%
  dplyr::pull(Id)

axys_males <- axys_metadata %>%
  dplyr::filter(Sex == "M") %>%
  dplyr::pull(Id)

# Donor IDs
axys_donors <- axys_metadata %>%
  dplyr::select(Id)

# Subset data by tissue type
subset_tissue <- function(tissue) {
  axys_pops_2 %>%
    dplyr::filter(!str_detect(COMPOUND, "Total"), TISSUE_TYPE == tissue) %>%
    dplyr::select(DONOR, COMPOUND, BLANK_and_LOD_adj) %>%
    group_by(DONOR) %>%
    pivot_wider(names_from = COMPOUND, values_from = BLANK_and_LOD_adj) %>%
    ungroup()
}

axys_pops_panc <- subset_tissue("Pancreas")
axys_pops_adip <- subset_tissue("Adipose")
```

# Load static GSIS and perifusion data

```{r}
# load GSIS data from ADI
gsis_adi_param <- read_excel(here::here("data", "Perifusion+GSIS", "2024-05-18_IsletCore_GSIS_from_TeamGrant_website.xlsx")) %>%
  mutate(Cond = factor(Cond, levels = c("1", "2", "3")),
                replicate = as.character(replicate))

gsis_adi_ave <- gsis_adi_param %>%
  mutate(across(4:ncol(.), as.numeric)) %>%
  group_by(Donor, Cond) %>%
  mutate(InsulinContent_IsletCore = mean(InsulinContent),
                LG_IsletCore = mean(LG, na.rm = TRUE),
                HG_IsletCore = mean(HG, na.rm = TRUE),
                SI_IsletCore = mean(SI, na.rm = TRUE),
                .keep = c("unused")) %>%
  distinct(Donor, Cond, .keep_all = TRUE) %>%
  dplyr::select(-replicate) %>%
  ungroup()
  
gsis_adi_wide <- gsis_adi_ave %>%
  pivot_wider(names_from = Cond, values_from = c(InsulinContent_IsletCore, LG_IsletCore, HG_IsletCore, SI_IsletCore)) %>%
  relocate(Donor, InsulinContent_IsletCore_1, LG_IsletCore_1, HG_IsletCore_1, SI_IsletCore_1,
           InsulinContent_IsletCore_2, LG_IsletCore_2, HG_IsletCore_2, SI_IsletCore_2,
           InsulinContent_IsletCore_3, LG_IsletCore_3, HG_IsletCore_3, SI_IsletCore_3)

# Load pre-GSIS total insulin content
gsis_adi_preInsCont <- read_csv(here::here("data", "Perifusion+GSIS", "2025-07-25_team_grant_website_isolation_info.csv")) %>%
  dplyr::select("record_id", "insulincontent") %>%
  mutate(PreInsulinContent_IsletCore = insulincontent,
                .keep = c("unused"))

# Combine pre-GSIS total insulin content with the rest of the dataset
gsis_adi <- gsis_adi_wide %>%
  left_join(., gsis_adi_preInsCont, by = c("Donor" = "record_id"))
```

```{r}
# Load perifusion data from Jelena Kolic
peri_jk <- read_excel(here::here("data", "Perifusion+GSIS", "2024-04-06_Jelena_all_perifusion_AUCs.xlsx")) %>%
  mutate(PerifusionParam = str_c("JK", PerifusionParam, sep = "_"),
                .keep = "unused") %>%
  mutate(across(4:ncol(.), as.numeric))

# Separate data based on perifusion type (glucose, leucine, oleate-pamlitate)
glu_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "GLU") %>%
  remove_empty("cols")

leu_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "LEU") %>%
  remove_empty("cols")

fa_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "OLE-PALM") %>%
  remove_empty("cols")

# Transpose for matrices
glu_peri_jk_t <- glu_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.) - 1)) %>%
  mutate(Donor = rownames(.), .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"), across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  mutate(across(2:ncol(.), as.numeric))


leu_peri_jk_t <- leu_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.) - 1)) %>%
  mutate(Donor = rownames(.), .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"), across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  mutate(across(2:ncol(.), as.numeric))

fa_peri_jk_t <- fa_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.) - 1)) %>%
  mutate(Donor = rownames(.), .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"), across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  mutate(across(2:ncol(.), as.numeric))
```

```{r}
# Load Myriam perifusion data
glu_peri_mh <- read_excel(here::here("data", "Perifusion+GSIS", "2024-01-25_Perifusion_FINAL DATA_For analysis_AC.xlsx")) %>%
  mutate(PerifusionParam = str_c("MH", PerifusionParam, sep = "_"),
         .keep = c("unused")) %>%
  mutate(across(3:ncol(.), as.numeric))

glu_peri_mh_t <- glu_peri_mh %>%
  dplyr::select(-MainOutcome) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor)
```

## Calculate analyte sums by class

```{r}
# Create compounds list by class
dioxin_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin") %>%
  dplyr::pull(Compound)

pcb_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "DL" | Dioxin_similarity == "NDL") %>%
  dplyr::pull(Compound)

ocp_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "OCP") %>%
  dplyr::pull(Compound)
```

```{r}
# Calculate sums for pancreas POPs
axys_panc_sum <- axys_pops_panc %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate pancreas PCB sum without PCB77
axys_panc_no_pcb77 <- axys_pops_panc %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine pancreas PCB sums without PCB77 with the rest of the sum data
axys_panc_sums <- axys_panc_sum %>%
  left_join(., axys_panc_no_pcb77, by = c("DONOR" = "DONOR"))
```

```{r}
# Calculate sums for adipose POPs
axys_adip_sum <- axys_pops_adip %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate adipose PCB sum without PCB77
axys_adip_no_pcb77 <- axys_pops_adip %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine adipose PCB sums without PCB77 with the rest of the sum data
axys_adip_sums <- axys_adip_sum %>%
  left_join(., axys_adip_no_pcb77, by = c("DONOR" = "DONOR"))
```

```{r}
# Calculate sums for pancreas POPs using imputed data
axys_panc_imputed_sum <- axys_pops_imputed_panc %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate pancreas PCB sum without PCB77 (imputed data)
axys_panc_no_pcb77_imputed <- axys_pops_imputed_panc %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine pancreas PCB sums without PCB77 with the rest of the sum data (imputed data)
axys_panc_imputed_sums <- axys_panc_imputed_sum %>%
  left_join(., axys_panc_no_pcb77_imputed, by = c("DONOR" = "DONOR"))
```

```{r}
# Calculate sums for adipose POPs using imputed data
axys_adip_imputed_sum <- axys_pops_imputed_adip %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate adipose PCB sum without PCB77 (imputed)
axys_adip_no_pcb77_imputed <- axys_pops_imputed_adip %>%
  pivot_longer(cols = -DONOR,
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine pancreas PCB sums without PCB77 with the rest of the sum data (imputed data)
axys_adip_imputed_sums <- axys_adip_imputed_sum %>%
  left_join(., axys_adip_no_pcb77_imputed, by = c("DONOR" = "DONOR"))
```

```{r}
# Combine single analyte concentrations with sums

# Data without imputations
axys_pops_with_sums_panc <- axys_pops_panc %>%
  left_join(., axys_panc_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip <- axys_pops_adip %>%
  left_join(., axys_adip_sums, by = c("DONOR" = "DONOR"))

# Imputed data
axys_pops_with_sums_panc_imputed <- axys_pops_imputed_panc %>%
  left_join(., axys_panc_imputed_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip_imputed <- axys_pops_imputed_adip %>%
  left_join(., axys_adip_imputed_sums, by = c("DONOR" = "DONOR"))
```

```{r}
# Combine analyte concentrations with metadata
axys_pops_with_sums_panc_meta <- axys_pops_with_sums_panc %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta <- axys_pops_with_sums_adip %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_panc_meta_imputed <- axys_pops_with_sums_panc_imputed %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta_imputed <- axys_pops_with_sums_adip_imputed %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)
```

# Sensitivity analyses

For sensitivity analyses, I am comparing the correlation coefficients from the original dataset with correlation coefficients after the following adjustments: (1) imputing missing pollutant concentration values, or (2) removing one or more influential donors. Influential donors were donors that did not cluster with the rest of the donor population in PCA analyses.

```{r}
# Remove outlier donors
rm_ind_adip <- c("R419", "R421")
rm_ind_panc <- c("R389", "R419", "R448")
```

## Create a dataframe for pollutant concentration data by tissue type and pollutant class

I generated a separate dataframe of pollutant concentration data by pollutant class for each tissue. I made 5 to 6 dataframes per pollutant class per tissue: (1) unadjusted data (i.e., no imputations, no donors excluded), (2) data with imputed missing values: "_imp", (3) data with all outliers removed: "_panc_rm_ind" or "_adip_rm_ind", (4) data with one influential donor removed at a time. There were 3 influential donors in pancreas ("_rm_R389", "_rm_R419", or "_rm_R448") and 2 influential donors in adipose ("_rm_R419" or "_rm_R421").

### Dioxins: Pancreas

```{r}
# All donors
axys_pops_panc_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

# Separated by sex
axys_pops_panc_dioxin_F <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_dioxin_M <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

# All donors with imputed values or donors removed
axys_pops_panc_dioxin_imputed <- axys_pops_with_sums_panc_imputed %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_ind_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_389_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_419_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_panc_rm_448_dioxin <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)
```

### Dioxins: Adipose

```{r}
# All donors
axys_pops_adip_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

# Separated by sex
axys_pops_adip_dioxin_F <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_dioxin_M <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

# All donors with imputed values or donors removed
axys_pops_adip_dioxin_imputed <- axys_pops_with_sums_adip_imputed %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_rm_ind_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_rm_419_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_rm_421_dioxin <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)
```

### PCBs: Pancreas

```{r}
# All donors
axys_pops_panc_pcb <- axys_pops_with_sums_panc %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

# Separated by sex
axys_pops_panc_pcb_F <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_panc_pcb_M <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

# All donors with imputed values or donors removed
axys_pops_panc_pcb_imputed <- axys_pops_with_sums_panc_imputed %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_panc_rm_ind_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_panc_rm_389_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_panc_rm_419_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_panc_rm_448_pcb <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)
```

### PCBs: Adipose

```{r}
# All donors
axys_pops_adip_pcb <- axys_pops_with_sums_adip %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

# Separated by sex
axys_pops_adip_pcb_F <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_adip_pcb_M <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

# All donors with imputed values or donors removed
axys_pops_adip_pcb_imputed <- axys_pops_with_sums_adip_imputed %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_adip_rm_ind_pcb <- axys_pops_with_sums_adip %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_adip_rm_419_pcb <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)

axys_pops_adip_rm_421_pcb <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77)
```

### OCPs: Pancreas

```{r}
# All donors
axys_pops_panc_ocp <- axys_pops_with_sums_panc %>%
  dplyr::select(DONOR, any_of(ocp_list))

# Separated by sex
axys_pops_panc_ocp_F <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_ocp_M <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(ocp_list))

# All donors with imputed values or donors removed
axys_pops_panc_ocp_imputed <- axys_pops_with_sums_panc_imputed %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_ind_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_389_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_419_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_panc_rm_448_ocp <- axys_pops_with_sums_panc %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(ocp_list))
```

### OCPs: Adipose

```{r}
# All donors
axys_pops_adip_ocp <- axys_pops_with_sums_adip %>%
  dplyr::select(DONOR, any_of(ocp_list))

# Separated by sex
axys_pops_adip_ocp_F <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_ocp_M <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(ocp_list))

# All donors with imputed values or donors removed
axys_pops_adip_ocp_imputed <- axys_pops_with_sums_adip_imputed %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_rm_ind_ocp <- axys_pops_with_sums_adip %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_rm_419_ocp <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_rm_421_ocp <- axys_pops_with_sums_adip %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(ocp_list))
```

# Correlate concentrations of each analyte with each other within each tissue

## Create lists of concentration matrices for each tissue/POP subgroup

### Pancreas

```{r}
axys_analytes_list_panc <- list(
  axys_pops_panc_dioxin = axys_pops_panc_dioxin,
  axys_pops_panc_pcb = axys_pops_panc_pcb,
  axys_pops_panc_ocp = axys_pops_panc_ocp
)

axys_analytes_list_panc_F <- list(
  axys_pops_panc_dioxin_F = axys_pops_panc_dioxin_F,
  axys_pops_panc_pcb_F = axys_pops_panc_pcb_F,
  axys_pops_panc_ocp_F = axys_pops_panc_ocp_F
)

axys_analytes_list_panc_M <- list(
  axys_pops_panc_dioxin_M = axys_pops_panc_dioxin_M,
  axys_pops_panc_pcb_M = axys_pops_panc_pcb_M,
  axys_pops_panc_ocp_M = axys_pops_panc_ocp_M
)

axys_analytes_list_panc_imputed <- list(
  axys_pops_panc_dioxin_imputed = axys_pops_panc_dioxin_imputed,
  axys_pops_panc_pcb_imputed = axys_pops_panc_pcb_imputed,
  axys_pops_panc_ocp_imputed = axys_pops_panc_ocp_imputed
)

axys_analytes_list_panc_rm_ind <- list(
  axys_pops_panc_rm_ind_dioxin = axys_pops_panc_rm_ind_dioxin,
  axys_pops_panc_rm_ind_pcb = axys_pops_panc_rm_ind_pcb,
  axys_pops_panc_rm_ind_ocp = axys_pops_panc_rm_ind_ocp
)

axys_analytes_list_panc_rm_389 <- list(
  axys_pops_panc_rm_389_dioxin = axys_pops_panc_rm_389_dioxin,
  axys_pops_panc_rm_389_pcb = axys_pops_panc_rm_389_pcb,
  axys_pops_panc_rm_389_ocp = axys_pops_panc_rm_389_ocp
)

axys_analytes_list_panc_rm_419 <- list(
  axys_pops_panc_rm_419_dioxin = axys_pops_panc_rm_419_dioxin,
  axys_pops_panc_rm_419_pcb = axys_pops_panc_rm_419_pcb,
  axys_pops_panc_rm_419_ocp = axys_pops_panc_rm_419_ocp
)

axys_analytes_list_panc_rm_448 <- list(
  axys_pops_panc_rm_448_dioxin = axys_pops_panc_rm_448_dioxin,
  axys_pops_panc_rm_448_pcb = axys_pops_panc_rm_448_pcb,
  axys_pops_panc_rm_448_ocp = axys_pops_panc_rm_448_ocp
)
```

### Adipose

```{r}
axys_analytes_list_adip <- list(
  axys_pops_adip_dioxin = axys_pops_adip_dioxin,
  axys_pops_adip_pcb = axys_pops_adip_pcb,
  axys_pops_adip_ocp = axys_pops_adip_ocp
)

axys_analytes_list_adip_F <- list(
  axys_pops_adip_dioxin_F = axys_pops_adip_dioxin_F,
  axys_pops_adip_pcb_F = axys_pops_adip_pcb_F,
  axys_pops_adip_ocp_F = axys_pops_adip_ocp_F
)

axys_analytes_list_adip_M <- list(
  axys_pops_adip_dioxin_M = axys_pops_adip_dioxin_M,
  axys_pops_adip_pcb_M = axys_pops_adip_pcb_M,
  axys_pops_adip_ocp_M = axys_pops_adip_ocp_M
)

axys_analytes_list_adip_imputed <- list(
  axys_pops_adip_dioxin_imputed = axys_pops_adip_dioxin_imputed,
  axys_pops_adip_pcb_imputed = axys_pops_adip_pcb_imputed,
  axys_pops_adip_ocp_imputed = axys_pops_adip_ocp_imputed
)

axys_analytes_list_adip_rm_ind <- list(
  axys_pops_adip_rm_ind_dioxin = axys_pops_adip_rm_ind_dioxin,
  axys_pops_adip_rm_ind_pcb = axys_pops_adip_rm_ind_pcb,
  axys_pops_adip_rm_ind_ocp = axys_pops_adip_rm_ind_ocp
)

axys_analytes_list_adip_rm_419 <- list(
  axys_pops_adip_rm_419_dioxin = axys_pops_adip_rm_419_dioxin,
  axys_pops_adip_rm_419_pcb = axys_pops_adip_rm_419_pcb,
  axys_pops_adip_rm_419_ocp = axys_pops_adip_rm_419_ocp
)

axys_analytes_list_adip_rm_421 <- list(
  axys_pops_adip_rm_421_dioxin = axys_pops_adip_rm_421_dioxin,
  axys_pops_adip_rm_421_pcb = axys_pops_adip_rm_421_pcb,
  axys_pops_adip_rm_421_ocp = axys_pops_adip_rm_421_ocp
) 
```

```{r}
axys_analytes_all <- list(
  # Pancreas
  panc_orig       = axys_analytes_list_panc,
  panc_F          = axys_analytes_list_panc_F,
  panc_M          = axys_analytes_list_panc_M,
  panc_imputed    = axys_analytes_list_panc_imputed,
  panc_rm_ind     = axys_analytes_list_panc_rm_ind,
  panc_rm_389     = axys_analytes_list_panc_rm_389,
  panc_rm_419     = axys_analytes_list_panc_rm_419,
  panc_rm_448     = axys_analytes_list_panc_rm_448,
  
  # Adipose
  adip_orig       = axys_analytes_list_adip,
  adip_F          = axys_analytes_list_adip_F,
  adip_M          = axys_analytes_list_adip_M,
  adip_imputed    = axys_analytes_list_adip_imputed,
  adip_rm_ind     = axys_analytes_list_adip_rm_ind,
  adip_rm_419     = axys_analytes_list_adip_rm_419,
  adip_rm_421     = axys_analytes_list_adip_rm_421
)

corr_results_ci <- purrr::map(axys_analytes_all, ~ apply_r(.x, output = "ci"))
corr_results_upper <- purrr::map(axys_analytes_all, ~ apply_r(.x, output = "upper"))

# save_correlation_matrices(corr_results_ci, write_metadata = FALSE)
# save_correlation_matrices(corr_results_upper, write_metadata = FALSE)
```

```{r, fig.width = 8, dpi = 100}
# Perform kendall correlations for all combinations of axys analytes vs analytes
axys_analytes_all_corr <- imap(axys_analytes_all, ~ map(.x, cor.mtest))
    # Nested lists: outer = tissue/version (e.g., orig, F/M, imputed), inner = pollutant class
    # cor.mtest is applied to each analyte matrix

# Plot each correlation result
# walk(axys_analytes_all_corr, ~ plot_all_correlations(.x))

# Export plots
# imap(axys_analytes_all_corr, ~ plot_all_correlations(.x, file.path("corr_plots_pop_vs_pop", .y), width = 8, height = 6, res = 300))
```

## Calculate percent change in correlation coefficient

```{r}
# generate_rchange_lists(
#   nested_corr_list = corr_results_ci[!names(corr_results_ci) %in% c("adip_F", "adip_M")],
#   tissue = "adip",
#   save_csv = TRUE,
#   out_dir = paste0(Sys.Date(), "_pops_vs_pops_rchange/adipose")
# )
# 
# generate_rchange_lists(
#   nested_corr_list = corr_results_ci[!names(corr_results_ci) %in% c("panc_F", "panc_M")],
#   tissue = "panc",
#   save_csv = TRUE,
#   out_dir = paste0(Sys.Date(), "_pops_vs_pops_rchange/pancreas")
# )
```

## Combine analyte concentrations with GSIS data

I generated a separate dataframe of pollutant concentration data + GSIS data by pollutant class for each tissue. There are 5 sets of GSIS parameter data: (1) static GSIS data from ADI, (2) glucose perifusion data from JK, (3) leucine perifusion data from JK, (4) fatty acid perifusion data from JK, (5) glucose perifusion data from MH.

For each combination of GSIS dataset and pollutant class in each tissue, there are 5 to 6 dataframes with: (1) unadjusted data (i.e., no imputations, no donors excluded), (2) data with imputed missing values: "_imputed", (3) data with all outliers removed: "_panc_rm_ind" or "_adip_rm_ind", (4) data with one influential donor removed at a time. There were 3 influential donors in pancreas ("_rm_R389", "_rm_R419", or "_rm_R448") and 2 influential donors in adipose ("_rm_R419" or "_rm_R421").

```{r}
# Join function for combining analyte dataframes with functional parameters
join_gsis_data <- function(exposure_df, gsis_target_list, convert_numeric = FALSE) {
  purrr::imap(gsis_target_list, function(gsis_df, suffix) {
    result <- dplyr::left_join(exposure_df, gsis_df, by = c("DONOR" = "Donor"))
    if (convert_numeric) {
      result <- result %>% dplyr::mutate(across(2:ncol(.), as.numeric))
    }
    result
  })
}
```

```{r}
# GSIS parameters
gsis_parameters <- list(
  core     = gsis_adi,
  jk_glu   = glu_peri_jk_t,
  jk_leu   = leu_peri_jk_t,
  jk_fa    = fa_peri_jk_t,
  mh_glu   = glu_peri_mh_t
)

# Dioxins
panc_dioxin_vers <- list(
  orig     = axys_pops_panc_dioxin,
  females  = axys_pops_panc_dioxin_F,
  males    = axys_pops_panc_dioxin_M,
  imputed  = axys_pops_panc_dioxin_imputed,
  rm_ind   = axys_pops_panc_rm_ind_dioxin,
  rm_389   = axys_pops_panc_rm_389_dioxin,
  rm_419   = axys_pops_panc_rm_419_dioxin,
  rm_448   = axys_pops_panc_rm_448_dioxin
)

adip_dioxin_vers <- list(
  orig    = axys_pops_adip_dioxin,
  females = axys_pops_adip_dioxin_F,
  males   = axys_pops_adip_dioxin_M,
  imputed = axys_pops_adip_dioxin_imputed,
  rm_ind  = axys_pops_adip_rm_ind_dioxin,
  rm_419  = axys_pops_adip_rm_419_dioxin,
  rm_421  = axys_pops_adip_rm_421_dioxin
)

# PCBs
panc_pcb_vers <- list(
  orig    = axys_pops_panc_pcb,
  females = axys_pops_panc_pcb_F,
  males   = axys_pops_panc_pcb_M,
  imputed = axys_pops_panc_pcb_imputed,
  rm_ind  = axys_pops_panc_rm_ind_pcb,
  rm_389  = axys_pops_panc_rm_389_pcb,
  rm_419  = axys_pops_panc_rm_419_pcb,
  rm_448  = axys_pops_panc_rm_448_pcb
)

adip_pcb_vers <- list(
  orig    = axys_pops_adip_pcb,
  females = axys_pops_adip_pcb_F,
  males   = axys_pops_adip_pcb_M,
  imputed = axys_pops_adip_pcb_imputed,
  rm_ind  = axys_pops_adip_rm_ind_pcb,
  rm_419  = axys_pops_adip_rm_419_pcb,
  rm_421  = axys_pops_adip_rm_421_pcb
)

# OCPs
panc_ocp_vers <- list(
  orig    = axys_pops_panc_ocp,
  females = axys_pops_panc_ocp_F,
  males   = axys_pops_panc_ocp_M,
  imputed = axys_pops_panc_ocp_imputed,
  rm_ind  = axys_pops_panc_rm_ind_ocp,
  rm_389  = axys_pops_panc_rm_389_ocp,
  rm_419  = axys_pops_panc_rm_419_ocp,
  rm_448  = axys_pops_panc_rm_448_ocp
)

adip_ocp_vers <- list(
  orig    = axys_pops_adip_ocp,
  females = axys_pops_adip_ocp_F,
  males   = axys_pops_adip_ocp_M,
  imputed = axys_pops_adip_ocp_imputed,
  rm_ind  = axys_pops_adip_rm_ind_ocp,
  rm_419  = axys_pops_adip_rm_419_ocp,
  rm_421  = axys_pops_adip_rm_421_ocp
)
```

```{r}
joined_panc_dioxin <- map(panc_dioxin_vers, ~ join_gsis_data(.x, gsis_parameters, convert_numeric = TRUE))
joined_adip_dioxin <- map(adip_dioxin_vers, ~ join_gsis_data(.x, gsis_parameters, convert_numeric = TRUE))

joined_panc_pcb <- map(panc_pcb_vers, ~ join_gsis_data(.x, gsis_parameters, convert_numeric = TRUE))
joined_adip_pcb <- map(adip_pcb_vers, ~ join_gsis_data(.x, gsis_parameters, convert_numeric = TRUE))

joined_panc_ocp <- map(panc_ocp_vers, ~ join_gsis_data(.x, gsis_parameters, convert_numeric = TRUE))
joined_adip_ocp <- map(adip_ocp_vers, ~ join_gsis_data(.x, gsis_parameters, convert_numeric = TRUE))
```

```{r}
# Note: assigns many joined exposure+GSIS dataframes into .GlobalEnv
#   e.g., axys_pops_panc_dioxin_orig_core, axys_pops_panc_dioxin_orig_jk_glu, etc.

assign_joined_dfs <- function(joined_list, prefix) {
  walk2(names(joined_list), joined_list, function(version_name, inner_list) {
    walk2(names(inner_list), inner_list, function(panel_name, df) {
      assign(paste0(prefix, "_", version_name, "_", panel_name), df, envir = .GlobalEnv)
    })
  })
}

assign_joined_dfs(joined_panc_dioxin, "axys_pops_panc_dioxin")
assign_joined_dfs(joined_adip_dioxin, "axys_pops_adip_dioxin")
assign_joined_dfs(joined_panc_pcb, "axys_pops_panc_pcb")
assign_joined_dfs(joined_adip_pcb, "axys_pops_adip_pcb")
assign_joined_dfs(joined_panc_ocp, "axys_pops_panc_ocp")
assign_joined_dfs(joined_adip_ocp, "axys_pops_adip_ocp")
```

## Correlate analyte concentrations with functional parameters

```{r}
# Generate list of pollutant x GSIS parameter combinations
generate_gsis_pollutant_lists(tissue = "panc")
generate_gsis_pollutant_lists(tissue = "adip")
```

```{r}
# Export results to csv
# run_all_corr_tests_on_lists(
#   tissue = "panc",
#   save_csv = TRUE,
#   export_r_matrix = TRUE,
#   export_p_matrix = FALSE,
#   out_dir = file.path(paste0(Sys.Date(), "_pops_vs_GSIS"), "pancreas")
# )
# 
# run_all_corr_tests_on_lists(
#   tissue = "adip",
#   save_csv = TRUE,
#   export_r_matrix = TRUE,
#   export_p_matrix = FALSE,
#   out_dir = file.path(paste0(Sys.Date(), "_pops_vs_GSIS"), "adipose")
# )

# ls(pattern = "^axys_pops_with_sums_panc_.*_list$")
```

```{r}
# Perform correlations for plotting
corr_results_panc <- run_all_corr_tests_on_lists(tissue = "panc", methods = "cor.mtest")
corr_results_adip <- run_all_corr_tests_on_lists(tissue = "adip", methods = "cor.mtest")
```

### Correlation plots

```{r, fig.width = 18, dpi = 100}
# Plot each correlation result: pancreas
# walk(corr_results_panc, ~ plot_all_correlations(.x))

# Export plots
# imap(corr_results_panc, ~ plot_all_correlations(.x, file.path("corr_plots_pop_vs_gsis_panc", .y), width = 12, height = 10, res = 300))
```

```{r, fig.width = 18, dpi = 100}
# Plot each correlation result: adipose
# walk(corr_results_adip, ~ plot_all_correlations(.x))

# Export plots
# imap(corr_results_adip, ~ plot_all_correlations(.x, file.path("corr_plots_pop_vs_gsis_adip", .y), width = 12, height = 10, res = 300))
```

## Calculate percent change in correlation coefficient

```{r}
# run_all_gsis_correlations(save_csv = TRUE, out_dir = file.path(paste0(Sys.Date(), "_pops_vs_GSIS_rchange")))
```

# Session Info

```{r}
sessionInfo()
```
