---
title: "Correlating AXYS pollutant concentrations with donor characteristics"
author: "Angela Ching"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: yes
---

# Notes from MH

IsletCore GSIS:
- Condition #1 = LG 2.8mM, HG 16.7mM 
- Condition #2 = LG 1mM, HG 16.7mM
- Condition #3 = LG 1mM, HG 10mM

Perifusion:
- Exclude KCl for donors: R361, R362, R385, R391 (already removed from final excel)
- Only use basal LG (exclude the rest of perifusion curve) for donors: R419, R421 (already removed from final excel)

Exclusion criteria
- Remove any analyte with >50% donors below LOD
- Remove any analyte with >40% of donors with NDR flag

# Packages

```{r packages}
library(tidyverse)    # contains ggplot2, purrr, etc.
library(readxl)
library(janitor)      # for data cleaning
library(scico)        # colour palettes
library(ggsci)        # colour palettes
library(ggpubr)       # for scatterplot correlations
library(psychometric) # masks "select" from dplyr; for CIr()
library(reshape2)     # for reshaping data for heatmaps
library(knitr)
library(pheatmap)
library(corrplot)
library(psych)
library(lme4)
library(here)
```

# Load necessary functions

```{r}
source(here::here("functions", "correlation_functions.R")) # General correlation functions
source(here::here("functions", "plotting_functions.R"))    # Plotting functions
source(here::here("functions", "percent_change.R"))        # Calculate percent change (sensitivity analyses)
source(here::here("functions", "correlations_gsis.R"))     # Correlate analyte concentrations with different GSIS parameters
```

# Load data

```{r}
# load chemical list
chem_list <- read_csv(here::here("data", "2022-10-18_pops_analytes_list.csv")) %>%
  dplyr::select(Compound, Dioxin_subtype) %>%
  mutate(across(where(is.character), str_squish))

chem_list_2 <- read_csv(here::here("data", "2024-10-01_pops_list_with_coelutions.csv")) %>%
  dplyr::select(-c(Dioxin_subtype, Type)) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS data
axys_pops <- read_csv(here::here("data", "2024-08-24_pops_data_outliers_excluded_for_single_analyte_analyses.csv")) %>%
  dplyr::select(-c(CONC_BLANK_adj, IS_BLANK_ADJ_CONC_HIGHER_THAN_LOD)) %>%
  mutate(BLANK_and_LOD_adj = as.numeric(BLANK_and_LOD_adj),
         File = factor(File),
         COMPOUND = case_when(str_detect(COMPOUND, "TOTAL") ~ str_to_sentence(COMPOUND),
                              str_detect(COMPOUND, " Epoxide") ~ str_to_sentence(COMPOUND),
                              TRUE ~ COMPOUND),
         across(where(is.character), str_squish))

axys_pops_2 <- axys_pops %>%
  dplyr::select(-c(File, LAB_FLAG, DETECTION_LIMIT)) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS data with imputed values for true NAs (chemicals not measured by AXYS in certain donors)
axys_pops_imputed_panc <- read_excel(here::here("outputs", "2024-09-03_pops_with_imputed_values.xlsx"), sheet = 1) %>%
  mutate(across(where(is.character), str_squish))

axys_pops_imputed_adip <- read_excel(here::here("outputs", "2024-09-03_pops_with_imputed_values.xlsx"),sheet = 2) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS donor metadata
axys_metadata <- read_csv(here::here("data", "2024-08-22_donor_characteristics.csv"),show_col_types = FALSE) %>%
  mutate(BMI_category = case_when(BMI < 24.9 ~ "Lean",
                                  BMI >= 24.9 & BMI <= 29.9 ~ "Overweight",
                                  BMI > 29.9 ~ "Obese"),
         Hba1c_category = case_when(Hba1c < 6 ~ "Normoglycemic",
                                    Hba1c <= 6.5 ~ "Prediabetic",
                                    Hba1c > 6.5 ~ "Diabetic"),
         BMI_category = factor(BMI_category, levels = c("Lean", "Overweight", "Obese")),
         Hba1c_category = factor(Hba1c_category, levels = c("Normoglycemic", "Prediabetic", "Diabetic")),
         Sex = as_factor(Sex),
         Diabetes_status = as_factor(Diabetes_status)) %>%
  dplyr::select(-Purity)

# Subset data by sex
axys_females <- axys_metadata %>%
  dplyr::filter(Sex == "F") %>%
  dplyr::pull(Id)

axys_males <- axys_metadata %>%
  dplyr::filter(Sex == "M") %>%
  dplyr::pull(Id)

# Donor IDs
axys_donors <- axys_metadata %>%
  dplyr::select(Id)

# Subset data by tissue type
subset_tissue <- function(tissue) {
  axys_pops_2 %>%
    dplyr::filter(!str_detect(COMPOUND, "Total"), TISSUE_TYPE == tissue) %>%
    dplyr::select(DONOR, COMPOUND, BLANK_and_LOD_adj) %>%
    group_by(DONOR) %>%
    pivot_wider(names_from = COMPOUND, values_from = BLANK_and_LOD_adj) %>%
    ungroup()
}

axys_pops_panc <- subset_tissue("Pancreas")
axys_pops_adip <- subset_tissue("Adipose")
```
## Calculate analyte sums by class

```{r}
# Create compounds list by class
dioxin_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin") %>%
  dplyr::pull(Compound)

pcb_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "DL" | Dioxin_similarity == "NDL") %>%
  dplyr::pull(Compound)

ocp_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "OCP") %>%
  dplyr::pull(Compound)
```

I calculated analyte sums using both the unimputed and imputed datasets for sensitivity analyses. 

```{r}
# Calculate sums for pancreas POPs
axys_panc_sum <- axys_pops_panc %>%
  pivot_longer(cols = c(2:34),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate pancreas PCB sum without PCB77
axys_panc_no_pcb77 <- axys_pops_panc %>%
  pivot_longer(cols = c(2:34),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine pancreas PCB sums without PCB77 with the rest of the sum data
axys_panc_sums <- axys_panc_sum %>%
  left_join(., axys_panc_no_pcb77, by = c("DONOR" = "DONOR"))
```

```{r}
# Calculate sums for adipose POPs
axys_adip_sum <- axys_pops_adip %>%
  pivot_longer(cols = c(2:42),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate adipose PCB sum without PCB77
axys_adip_no_pcb77 <- axys_pops_adip %>%
  pivot_longer(cols = c(2:42),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine adipose PCB sums without PCB77 with the rest of the sum data
axys_adip_sums <- axys_adip_sum %>%
  left_join(., axys_adip_no_pcb77, by = c("DONOR" = "DONOR"))
```

```{r}
# Calculate sums for pancreas POPs using imputed data
axys_panc_imputed_sum <- axys_pops_imputed_panc %>%
  pivot_longer(cols = c(2:34),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate pancreas PCB sum without PCB77 (imputed data)
axys_panc_no_pcb77_imputed <- axys_pops_imputed_panc %>%
  pivot_longer(cols = c(2:34),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine pancreas PCB sums without PCB77 with the rest of the sum data (imputed data)
axys_panc_imputed_sums <- axys_panc_imputed_sum %>%
  left_join(., axys_panc_no_pcb77_imputed, by = c("DONOR" = "DONOR"))
```

```{r}
# Calculate sums for adipose POPs using imputed data
axys_adip_imputed_sum <- axys_pops_imputed_adip %>%
  pivot_longer(cols = c(2:42),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB) %>%
  ungroup()

# Calculate adipose PCB sum without PCB77 (imputed)
axys_adip_no_pcb77_imputed <- axys_pops_imputed_adip %>%
  pivot_longer(cols = c(2:42),
               names_to = "COMPOUND",
               values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  dplyr::filter(Dioxin_similarity == "DL", COMPOUND != "PCB 77") %>%
  dplyr::select(DONOR, COMPOUND, ADJ_CONC) %>%
  group_by(DONOR) %>%
  mutate(DL_no77 = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, DL_no77) %>%
  summarise()

# Combine pancreas PCB sums without PCB77 with the rest of the sum data (imputed data)
axys_adip_imputed_sums <- axys_adip_imputed_sum %>%
  left_join(., axys_adip_no_pcb77_imputed, by = c("DONOR" = "DONOR"))
```

```{r}
# Combine single analyte concentrations with sums

# Data without imputations
axys_pops_with_sums_panc <- axys_pops_panc %>%
  left_join(., axys_panc_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip <- axys_pops_adip %>%
  left_join(., axys_adip_sums, by = c("DONOR" = "DONOR"))

# Imputed data
axys_pops_with_sums_panc_imputed <- axys_pops_imputed_panc %>%
  left_join(., axys_panc_imputed_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip_imputed <- axys_pops_imputed_adip %>%
  left_join(., axys_adip_imputed_sums, by = c("DONOR" = "DONOR"))
```

```{r}
# Combine analyte concentrations with metadata
axys_pops_with_sums_panc_meta <- axys_pops_with_sums_panc %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta <- axys_pops_with_sums_adip %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_panc_imputed_meta <- axys_pops_with_sums_panc_imputed %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_imputed_meta <- axys_pops_with_sums_adip_imputed %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)
```

# Sensitivity analyses

For sensitivity analyses, I am comparing the correlation coefficients from the original dataset with correlation coefficients after the following adjustments: (1) imputing missing pollutant concentration values, or (2) removing one or more influential donors. Influential donors were donors that did not cluster with the rest of the donor population in PCA analyses.

```{r}
# Remove outlier donors
rm_ind_adip <- c("R419", "R421")
rm_ind_panc <- c("R389", "R419", "R448")
```

## Create a dataframe for pollutant concentration data by tissue type and pollutant class

I generated a separate dataframe of pollutant concentration data by pollutant class for each tissue. I made 5 to 6 dataframes per pollutant class per tissue: (1) unadjusted data (i.e., no imputations, no donors excluded), (2) data with imputed missing values: "_imp", (3) data with all outliers removed: "_panc_rm_ind" or "_adip_rm_id", (4) data with one influential donor removed at a time. There were 3 influential donors in pancreas ("_rm_R389", "_rm_R419", or "_rm_R448") and 2 influential donors in adipose ("_rm_R419" or "_rm_R421").

### Dioxins: Pancreas

```{r}
# All donors
axys_pops_panc_dioxin_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

# Separated by sex
axys_pops_panc_dioxin_meta_F <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_panc_dioxin_meta_M <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

# All donors with imputed values or donors removed
axys_pops_panc_dioxin_imputed_meta <- axys_pops_with_sums_panc_imputed_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_panc_rm_ind_dioxin_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_panc_rm_389_dioxin_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_panc_rm_419_dioxin_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_panc_rm_448_dioxin_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)
```

### Dioxins: Adipose

```{r}
# All donors
axys_pops_adip_dioxin_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

# Separated by sex
axys_pops_adip_dioxin_meta_F <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_adip_dioxin_meta_M <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

# All donors with imputed values or donors removed
axys_pops_adip_dioxin_imputed_meta <- axys_pops_with_sums_adip_imputed_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_adip_rm_ind_dioxin_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_adip_rm_419_dioxin_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)

axys_pops_adip_rm_421_dioxin_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI, Hba1c)
```

### PCBs: Pancreas

```{r}
# All donors
axys_pops_panc_pcb_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

# Separated by sex
axys_pops_panc_pcb_meta_F <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_panc_pcb_meta_M <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

# All donors with imputed values or donors removed
axys_pops_panc_pcb_imputed_meta <- axys_pops_with_sums_panc_imputed_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_panc_rm_ind_pcb_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_panc_rm_389_pcb_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_panc_rm_419_pcb_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_panc_rm_448_pcb_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)
```

### PCBs: Adipose

```{r}
# All donors
axys_pops_adip_pcb_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

# Separated by sex
axys_pops_adip_pcb_meta_F <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_adip_pcb_meta_M <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

# All donors with imputed values or donors removed
axys_pops_adip_pcb_imputed_meta <- axys_pops_with_sums_adip_imputed_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_adip_rm_ind_pcb_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_adip_rm_419_pcb_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)

axys_pops_adip_rm_421_pcb_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, DL, NDL, DL_no77, Age, BMI, Hba1c)
```

### OCPs: Pancreas

```{r}
# All donors
axys_pops_panc_ocp_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

# Separated by sex
axys_pops_panc_ocp_meta_F <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_panc_ocp_meta_M <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

# All donors with imputed values or donors removed
axys_pops_panc_ocp_imputed_meta <- axys_pops_with_sums_panc_imputed_meta %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_panc_rm_ind_ocp_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(!(DONOR %in% rm_ind_panc)) %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_panc_rm_389_ocp_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R389") %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_panc_rm_419_ocp_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_panc_rm_448_ocp_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::filter(DONOR != "R448") %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)
```

### OCPs: Adipose

```{r}
# All donors
axys_pops_adip_ocp_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

# Separated by sex
axys_pops_adip_ocp_meta_F <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR %in% axys_females) %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_adip_ocp_meta_M <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR %in% axys_males) %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

# All donors with imputed values or donors removed
axys_pops_adip_ocp_imputed_meta <- axys_pops_with_sums_adip_imputed_meta %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_adip_rm_ind_ocp_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(!(DONOR %in% rm_ind_adip)) %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_adip_rm_419_ocp_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR != "R419") %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)

axys_pops_adip_rm_421_ocp_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::filter(DONOR != "R421") %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI, Hba1c)
```

# Correlate metadata with individual analyte concentrations and analyte sums: Kendall

## Create lists of concentration matrices for each tissue/POP subgroup

### Pancreas

```{r}
axys_analytes_list_panc_meta <- list(
  axys_pops_panc_dioxin_meta = axys_pops_panc_dioxin_meta,
  axys_pops_panc_pcb_meta = axys_pops_panc_pcb_meta,
  axys_pops_panc_ocp_meta = axys_pops_panc_ocp_meta
)

axys_analytes_list_panc_meta_F <- list(
  axys_pops_panc_dioxin_meta_F = axys_pops_panc_dioxin_meta_F,
  axys_pops_panc_pcb_meta_F = axys_pops_panc_pcb_meta_F,
  axys_pops_panc_ocp_meta_F = axys_pops_panc_ocp_meta_F
)

axys_analytes_list_panc_meta_M <- list(
  axys_pops_panc_dioxin_meta_M = axys_pops_panc_dioxin_meta_M,
  axys_pops_panc_pcb_meta_M = axys_pops_panc_pcb_meta_M,
  axys_pops_panc_ocp_meta_M = axys_pops_panc_ocp_meta_M
)

axys_analytes_list_panc_imputed_meta <- list(
  axys_pops_panc_dioxin_imputed_meta = axys_pops_panc_dioxin_imputed_meta,
  axys_pops_panc_pcb_imputed_meta = axys_pops_panc_pcb_imputed_meta,
  axys_pops_panc_ocp_imputed_meta = axys_pops_panc_ocp_imputed_meta
)

axys_analytes_list_panc_rm_ind_meta <- list(
  axys_pops_panc_rm_ind_dioxin_meta = axys_pops_panc_rm_ind_dioxin_meta,
  axys_pops_panc_rm_ind_pcb_meta = axys_pops_panc_rm_ind_pcb_meta,
  axys_pops_panc_rm_ind_ocp_meta = axys_pops_panc_rm_ind_ocp_meta
)

axys_analytes_list_panc_rm_389_meta <- list(
  axys_pops_panc_rm_389_dioxin_meta = axys_pops_panc_rm_389_dioxin_meta,
  axys_pops_panc_rm_389_pcb_meta = axys_pops_panc_rm_389_pcb_meta,
  axys_pops_panc_rm_389_ocp_meta = axys_pops_panc_rm_389_ocp_meta
)

axys_analytes_list_panc_rm_419_meta <- list(
  axys_pops_panc_rm_419_dioxin_meta = axys_pops_panc_rm_419_dioxin_meta,
  axys_pops_panc_rm_419_pcb_meta = axys_pops_panc_rm_419_pcb_meta,
  axys_pops_panc_rm_419_ocp_meta = axys_pops_panc_rm_419_ocp_meta
)

axys_analytes_list_panc_rm_448_meta <- list(
  axys_pops_panc_rm_448_dioxin_meta = axys_pops_panc_rm_448_dioxin_meta,
  axys_pops_panc_rm_448_pcb_meta = axys_pops_panc_rm_448_pcb_meta,
  axys_pops_panc_rm_448_ocp_meta = axys_pops_panc_rm_448_ocp_meta
)
```

### Adipose

```{r}
axys_analytes_list_adip_meta <- list(
  axys_pops_adip_dioxin_meta = axys_pops_adip_dioxin_meta,
  axys_pops_adip_pcb_meta = axys_pops_adip_pcb_meta,
  axys_pops_adip_ocp_meta = axys_pops_adip_ocp_meta
)

axys_analytes_list_adip_meta_F <- list(
  axys_pops_adip_dioxin_meta_F = axys_pops_adip_dioxin_meta_F,
  axys_pops_adip_pcb_meta_F = axys_pops_adip_pcb_meta_F,
  axys_pops_adip_ocp_meta_F = axys_pops_adip_ocp_meta_F
)

axys_analytes_list_adip_meta_M <- list(
  axys_pops_adip_dioxin_meta_M = axys_pops_adip_dioxin_meta_M,
  axys_pops_adip_pcb_meta_M = axys_pops_adip_pcb_meta_M,
  axys_pops_adip_ocp_meta_M = axys_pops_adip_ocp_meta_M
)

axys_analytes_list_adip_imputed_meta <- list(
  axys_pops_adip_dioxin_imputed_meta = axys_pops_adip_dioxin_imputed_meta,
  axys_pops_adip_pcb_imputed_meta = axys_pops_adip_pcb_imputed_meta,
  axys_pops_adip_ocp_imputed_meta = axys_pops_adip_ocp_imputed_meta
)

axys_analytes_list_adip_rm_ind_meta <- list(
  axys_pops_adip_rm_ind_dioxin_meta = axys_pops_adip_rm_ind_dioxin_meta,
  axys_pops_adip_rm_ind_pcb_meta = axys_pops_adip_rm_ind_pcb_meta,
  axys_pops_adip_rm_ind_ocp_meta = axys_pops_adip_rm_ind_ocp_meta
)

axys_analytes_list_adip_rm_419_meta <- list(
  axys_pops_adip_rm_419_dioxin_meta = axys_pops_adip_rm_419_dioxin_meta,
  axys_pops_adip_rm_419_pcb_meta = axys_pops_adip_rm_419_pcb_meta,
  axys_pops_adip_rm_419_ocp_meta = axys_pops_adip_rm_419_ocp_meta
)

axys_analytes_list_adip_rm_421_meta <- list(
  axys_pops_adip_rm_421_dioxin_meta = axys_pops_adip_rm_421_dioxin_meta,
  axys_pops_adip_rm_421_pcb_meta = axys_pops_adip_rm_421_pcb_meta,
  axys_pops_adip_rm_421_ocp_meta = axys_pops_adip_rm_421_ocp_meta
) 
```

```{r}
axys_analytes_all <- list(
  # Pancreas
  panc_orig       = axys_analytes_list_panc_meta,
  panc_F          = axys_analytes_list_panc_meta_F,
  panc_M          = axys_analytes_list_panc_meta_M,
  panc_imputed    = axys_analytes_list_panc_imputed_meta,
  panc_rm_ind     = axys_analytes_list_panc_rm_ind_meta,
  panc_rm_389     = axys_analytes_list_panc_rm_389_meta,
  panc_rm_419     = axys_analytes_list_panc_rm_419_meta,
  panc_rm_448     = axys_analytes_list_panc_rm_448_meta,
  
  # Adipose
  adip_orig       = axys_analytes_list_adip_meta,
  adip_F          = axys_analytes_list_adip_meta_F,
  adip_M          = axys_analytes_list_adip_meta_M,
  adip_imputed    = axys_analytes_list_adip_imputed_meta,
  adip_rm_ind     = axys_analytes_list_adip_rm_ind_meta,
  adip_rm_419     = axys_analytes_list_adip_rm_419_meta,
  adip_rm_421     = axys_analytes_list_adip_rm_421_meta
)

corr_results_ci <- purrr::map(axys_analytes_all, ~ apply_r(.x, output = "ci"))
corr_results_upper <- purrr::map(axys_analytes_all, ~ apply_r(.x, output = "upper"))

# save_correlation_matrices(corr_results_ci, write_metadata = FALSE)
# save_correlation_matrices(corr_results_upper, write_metadata = FALSE)
```

## Perform Kendall correlations

```{r, fig.width = 8}
# Perform kendall correlations for all combinations of axys analytes vs analytes
axys_analytes_all_corr <- imap(axys_analytes_all, ~ map(.x, cor.mtest))

# Plot each correlation result
walk(axys_analytes_all_corr, ~ plot_all_correlations(.x))

# Export plots
# imap(axys_analytes_all_corr, ~ plot_all_correlations(.x, file.path("corr_plots_pop_vs_meta", .y), width = 8, height = 6, res = 300))
```

## Calculate percent change in correlation coefficient

```{r}
# generate_rchange_lists(
#   nested_corr_list = corr_results_ci[!names(corr_results_ci) %in% c("adip_F", "adip_M")],
#   tissue = "adip",
#   save_csv = TRUE,
#   out_dir = paste0(Sys.Date(), "_pops_vs_metadata_rchange/adipose")
# )
# 
# generate_rchange_lists(
#   nested_corr_list = corr_results_ci[!names(corr_results_ci) %in% c("panc_F", "panc_M")],
#   tissue = "panc",
#   save_csv = TRUE,
#   out_dir = paste0(Sys.Date(), "_pops_vs_metadata_rchange/pancreas")
# )
```

# Session Info

```{r}
sessionInfo()
```
