---
title: "AXYS Project Grant: Partial Correlations"
author: "Angela Ching"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: yes
---

# Packages

```{r}
library(tidyverse)    # contains ggplot2, purrr, etc.
library(readxl)
library(janitor)      # for data cleaning
library(scico)        # colour palettes
library(ggsci)        # colour palettes
library(ggpubr)       # for scatterplot correlations
library(psychometric) # masks "select" from dplyr; for CIr()
library(reshape2)     # for reshaping data for heatmaps
library(knitr)
library(pheatmap)
library(corrplot)
library(psych)
library(lme4)
library(moments)
library(gridExtra)
library(ppcor)       # for partial correlations
library(here)
```

```{r}
source(here::here("functions", "correlation_functions.R"))       # General correlation functions
source(here::here("functions", "percent_change.R"))              # Calculate percent change (sensitivity analyses)
source(here::here("functions", "partial_correlation_functions.R"))
```

# Load AXYS data

```{r}
# load chemical list
chem_list <- read_csv(here::here("data", "2022-10-18_pops_analytes_list.csv")) %>%
  dplyr::select(Compound, Dioxin_subtype) %>%
  mutate(across(where(is.character), str_squish))

chem_list_2 <- read_csv(here::here("data", "2024-10-01_pops_list_with_coelutions.csv")) %>%
  dplyr::select(-c(Dioxin_subtype, Type)) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS data
axys_pops <- read_csv(here::here("data", "2024-08-24_pops_data_outliers_excluded_for_single_analyte_analyses.csv")) %>%
  dplyr::select(-c(CONC_BLANK_adj, IS_BLANK_ADJ_CONC_HIGHER_THAN_LOD)) %>%
  mutate(BLANK_and_LOD_adj = as.numeric(BLANK_and_LOD_adj),
         File = factor(File),
         COMPOUND = case_when(str_detect(COMPOUND, "TOTAL") ~ str_to_sentence(COMPOUND),
                              str_detect(COMPOUND, " Epoxide") ~ str_to_sentence(COMPOUND),
                              TRUE ~ COMPOUND),
         across(where(is.character), str_squish))

axys_pops_2 <- axys_pops %>%
  dplyr::select(-c(File, LAB_FLAG, DETECTION_LIMIT)) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS data with imputed values for true NAs (chemicals not measured by AXYS in certain donors)
axys_pops_imputed_panc <- read_excel(here::here("data", "2024-09-03_pops_with_imputed_values.xlsx"), sheet = 1) %>%
  mutate(across(where(is.character), str_squish))

axys_pops_imputed_adip <- read_excel(here::here("data", "2024-09-03_pops_with_imputed_values.xlsx"), sheet = 2) %>%
  mutate(across(where(is.character), str_squish))

# load AXYS donor metadata
axys_metadata <- read_csv(here::here("data", "2024-08-22_donor_characteristics_FINAL.csv"),show_col_types = FALSE) %>%
  mutate(BMI_category = case_when(BMI < 24.9 ~ "Lean",
                                  BMI >= 24.9 & BMI <= 29.9 ~ "Overweight",
                                  BMI > 29.9 ~ "Obese"),
         Hba1c_category = case_when(Hba1c < 6 ~ "Normoglycemic",
                                    Hba1c <= 6.5 ~ "Prediabetic",
                                    Hba1c > 6.5 ~ "Diabetic"),
         BMI_category = factor(BMI_category, levels = c("Lean", "Overweight", "Obese")),
         Hba1c_category = factor(Hba1c_category, levels = c("Normoglycemic", "Prediabetic", "Diabetic")),
         Sex = as_factor(Sex),
         Diabetes_status = as_factor(Diabetes_status)) %>%
  dplyr::select(-Purity)

# Donor IDs
axys_donors <- axys_metadata %>%
  dplyr::select(Id)

# Subset data by tissue type
subset_tissue <- function(tissue) {
  axys_pops_2 %>%
    dplyr::filter(!str_detect(COMPOUND, "Total"), TISSUE_TYPE == tissue) %>%
    dplyr::select(DONOR, COMPOUND, BLANK_and_LOD_adj) %>%
    group_by(DONOR) %>%
    pivot_wider(names_from = COMPOUND, values_from = BLANK_and_LOD_adj) %>%
    ungroup()
}

axys_pops_panc <- subset_tissue("Pancreas")
axys_pops_adip <- subset_tissue("Adipose")
```

# Load data on glucose parameters

## ADI Islet Core: Static GSIS

```{r}
# load GSIS data from ADI
gsis_adi_param <- read_excel(here::here("data", "2024-05-18_isletcore_static_gsis.xlsx")) %>%
  dplyr::mutate(Cond = factor(Cond, levels = c("1", "2", "3")),
                replicate = as.character(replicate))

gsis_adi_ave <- gsis_adi_param %>%
  mutate(across(4:ncol(.), as.numeric)) %>%
  group_by(Donor, Cond) %>%
  dplyr::mutate(InsulinContent_IsletCore = mean(InsulinContent),
                LG_IsletCore = mean(LG, na.rm = TRUE),
                HG_IsletCore = mean(HG, na.rm = TRUE),
                SI_IsletCore = mean(SI, na.rm = TRUE),
                .keep = c("unused")) %>%
  distinct(Donor, Cond, .keep_all = TRUE) %>%
  dplyr::select(-replicate) %>%
  ungroup()
  
gsis_adi_wide <- gsis_adi_ave %>%
  pivot_wider(names_from = Cond, values_from = c(InsulinContent_IsletCore, LG_IsletCore, HG_IsletCore, SI_IsletCore)) %>%
  relocate(Donor, InsulinContent_IsletCore_1, LG_IsletCore_1, HG_IsletCore_1, SI_IsletCore_1,
           InsulinContent_IsletCore_2, LG_IsletCore_2, HG_IsletCore_2, SI_IsletCore_2,
           InsulinContent_IsletCore_3, LG_IsletCore_3, HG_IsletCore_3, SI_IsletCore_3)

# Load pre-GSIS total insulin content
gsis_adi_preInsCont <- read_csv(here::here("data", "2025-07-25_isolation_info.csv")) %>%
  dplyr::select("record_id", "insulincontent") %>%
  dplyr::mutate(PreInsulinContent_IsletCore = insulincontent,
                .keep = c("unused"))

# Combine pre-GSIS total insulin content with the rest of the dataset
gsis_adi <- gsis_adi_wide %>%
  left_join(., gsis_adi_preInsCont, by = c("Donor" = "record_id"))
```

## Jelena Kolic: Glucose, leucine, and fatty acid perifusions

```{r}
# Load perifusion data from Jelena Kolic
peri_jk <- read_excel(here::here("data", "2024-04-06_johnson_lab_perifusion.xlsx")) %>%
 dplyr::mutate(PerifusionParam = str_c("JK", PerifusionParam, sep = "_"),
         .keep = "unused") %>%
  mutate(across(4:ncol(.), as.numeric))

# Separate data based on perifusion type (glucose, leucine, oleate-pamlitate)
glu_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "GLU") %>%
  remove_empty("cols")

leu_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "LEU") %>%
  remove_empty("cols")

fa_peri_jk <- peri_jk %>%
  dplyr::filter(Secretagogue == "OLE-PALM") %>%
  remove_empty("cols")

# Transpose for matrices
glu_peri_jk_t <- glu_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  dplyr::filter(Donor %in% axys_donors$Id) %>%
  dplyr::mutate(across(2:ncol(.), as.numeric))

leu_peri_jk_t <- leu_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  dplyr::filter(Donor %in% axys_donors$Id) %>%
  dplyr::mutate(across(2:ncol(.), as.numeric))

fa_peri_jk_t <- fa_peri_jk %>%
  dplyr::select(-c(MainOutcome, Secretagogue)) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  dplyr::filter(Donor %in% axys_donors$Id) %>%
  dplyr::mutate(across(2:ncol(.), as.numeric))
```

## Bruin Lab: Glucose perifusion

```{r}
# Load Myriam perifusion data
glu_peri_mh <- read_excel(here::here("data", "2024-01-25_bruin_lab_glucose_perifusion.xlsx")) %>%
  mutate(PerifusionParam = str_c("MH", PerifusionParam, sep = "_"),
         .keep = c("unused")) %>%
  mutate(across(3:ncol(.), as.numeric))

glu_peri_mh_t <- glu_peri_mh %>%
  dplyr::select(-MainOutcome) %>%
  t() %>%
  as.data.frame() %>%
  set_names(.[1, ]) %>%
  slice_tail(., n = (nrow(.)-1)) %>%
  mutate(Donor = rownames(.),
         .keep = c("unused")) %>%
  mutate(Donor = str_remove(Donor, pattern = "Donor"),
         across(where(is.character), str_squish)) %>%
  relocate(Donor) %>%
  dplyr::filter(Donor %in% axys_donors$Id) %>%
  dplyr::mutate(across(2:ncol(.), as.numeric))
```

# Analysis prep

## Create compounds lists by class

```{r}
# Create compounds list by class
dioxin_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "Dioxin") %>%
  dplyr::pull(Compound) %>%
  c("Dioxin")

pcb_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "DL" | Dioxin_similarity == "NDL") %>%
  dplyr::pull(Compound) %>%
  c("PCB", "DL", "NDL")

ocp_list <- chem_list_2 %>%
  dplyr::filter(Dioxin_similarity == "OCP") %>%
  dplyr::pull(Compound)

# Create a list of vectors of analyte names
analyte_groups <- list(
  dioxin = dioxin_list,   
  pcb    = pcb_list,      
  ocp    = ocp_list       
)
```

## Create GSIS parameters list by type

```{r}
gsis_adi_list <- names(dplyr::select(gsis_adi, -Donor))
glu_peri_jk_list <- names(dplyr::select(glu_peri_jk_t, -Donor))
leu_peri_jk_list <- names(dplyr::select(leu_peri_jk_t, -Donor))
fa_peri_jk_list <- names(dplyr::select(fa_peri_jk_t, -Donor))
glu_peri_mh_list <- names(dplyr::select(glu_peri_mh_t, -Donor))

# Create a list of vectors with GSIS parameter names by type
gsis_groups <- list(
  core   = gsis_adi_list,
  jk_glu = glu_peri_jk_list,
  jk_leu = leu_peri_jk_list,
  jk_fa  = fa_peri_jk_list,
  mh_glu = glu_peri_mh_list
)
```

## Calculate dioxin and PCB sums

```{r}
# Calculate sums
axys_panc_sums <- axys_pops_panc %>%
  pivot_longer(cols = 2:ncol(.), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB)

axys_adip_sums <- axys_pops_adip %>%
  pivot_longer(cols = 2:ncol(.), names_to = "COMPOUND", values_to = "ADJ_CONC") %>%
  left_join(., chem_list_2, by = c("COMPOUND" = "Compound")) %>%
  group_by(DONOR, Dioxin_similarity) %>%
  mutate(AnalyteSums = sum(ADJ_CONC, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(DONOR, Dioxin_similarity, AnalyteSums) %>%
  summarise() %>%
  pivot_wider(names_from = Dioxin_similarity, values_from = AnalyteSums) %>%
  mutate(PCB = rowSums(across(c("DL", "NDL")))) %>%
  dplyr::select(-OCP) %>%
  relocate(DONOR, Dioxin, PCB)
```

```{r}
# Combine single analyte concentrations with sums
axys_pops_with_sums_panc <- axys_pops_panc %>%
  left_join(., axys_panc_sums, by = c("DONOR" = "DONOR"))

axys_pops_with_sums_adip <- axys_pops_adip %>%
  left_join(., axys_adip_sums, by = c("DONOR" = "DONOR"))

# Combine single analyte concentrations with metadata
axys_pops_with_sums_panc_meta <- axys_pops_with_sums_panc %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)

axys_pops_with_sums_adip_meta <- axys_pops_with_sums_adip %>%
  left_join(., axys_metadata, by = c("DONOR" = "Id")) %>%
  dplyr::select(-Hba1c_category)
```

## Create separate dataframes for each pollutant class

```{r}
## Pancreas and adipose POPs without metadata

# Dioxins
axys_pops_panc_dioxin <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

axys_pops_adip_dioxin <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin)

# PCBs
axys_pops_panc_pcb <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "DL", "NDL")

axys_pops_adip_pcb <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "DL", "NDL")

# OCPs
axys_pops_panc_ocp <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(ocp_list))

axys_pops_adip_ocp <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(ocp_list))
```

```{r}
## POPs with metadata

# Dioxins
axys_pops_panc_dioxin_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI)

axys_pops_adip_dioxin_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(dioxin_list), Dioxin, Age, BMI)

# PCBs
axys_pops_panc_pcb_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "DL", "NDL", Age, BMI)

axys_pops_adip_pcb_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(pcb_list), PCB, "DL", "NDL", Age, BMI)

# OCPs
axys_pops_panc_ocp_meta <- axys_pops_with_sums_panc_meta %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI)

axys_pops_adip_ocp_meta <- axys_pops_with_sums_adip_meta %>%
  dplyr::select(DONOR, any_of(ocp_list), Age, BMI)
```

# Partial correlations

## Correlate analyte concentrations within each pollutant class

```{r}
## Create lists with the combined dataframes (POPs data + donor characteristics)
# Pancreas
axys_pops_with_sums_panc_with_meta_list <- list(
  axys_pops_panc_dioxin_meta = axys_pops_panc_dioxin_meta,
  axys_pops_panc_pcb_meta = axys_pops_panc_pcb_meta,
  axys_pops_panc_ocp_meta = axys_pops_panc_ocp_meta
)

# Adipose
axys_pops_with_sums_adip_with_meta_list <- list(
  axys_pops_adip_dioxin_meta = axys_pops_adip_dioxin_meta,
  axys_pops_adip_pcb_meta = axys_pops_adip_pcb_meta,
  axys_pops_adip_ocp_meta = axys_pops_adip_ocp_meta
)
```

```{r}
# Perform partial correlations
out_panc_pops <- partial_ppcor_pops(
  pops_list      = axys_pops_with_sums_panc_with_meta_list,
  analyte_groups = analyte_groups,
  tissue_label   = "Pancreas",
  method         = "kendall",
  fdr_scope      = "within",
  symmetric      = TRUE,     
  donor_col      = "DONOR"
)

out_adip_pops <- partial_ppcor_pops(
  pops_list      = axys_pops_with_sums_adip_with_meta_list,
  analyte_groups = analyte_groups,
  tissue_label   = "Adipose",
  method         = "kendall",
  fdr_scope      = "within",
  symmetric      = TRUE,     
  donor_col      = "DONOR"
)
```

## Correlate analyte concentrations with GSIS parameters

```{r}
# Create list of dataframes with analyte concentrations by pollutant class
pops_meta_dfs_panc <- list(
  dioxin = axys_pops_panc_dioxin_meta,
  pcb    = axys_pops_panc_pcb_meta,
  ocp    = axys_pops_panc_ocp_meta
)

pops_meta_dfs_adip <- list(
  dioxin = axys_pops_adip_dioxin_meta,
  pcb    = axys_pops_adip_pcb_meta,
  ocp    = axys_pops_adip_ocp_meta
)

gsis_types <- list(
  core   = gsis_adi,
  jk_glu = glu_peri_jk_t,
  jk_leu = leu_peri_jk_t,
  jk_fa  = fa_peri_jk_t,
  mh_glu = glu_peri_mh_t
)
```

```{r}
# Join function for combining analyte dataframes with functional parameters
join_gsis_data <- function(exposure_df, gsis_target_list, convert_numeric = FALSE) {
  purrr::imap(gsis_target_list, function(gsis_df, suffix) {
    result <- dplyr::left_join(exposure_df, gsis_df, by = c("DONOR" = "Donor"))
    if (convert_numeric) {
      result <- result %>% dplyr::mutate(across(2:ncol(.), as.numeric))
    }
    result
  })
}
```

```{r}
# Join dataframes
pops_with_gsis_panc <- imap(pops_meta_dfs_panc, ~ join_gsis_data(.x, gsis_types, convert_numeric = TRUE))
pops_with_gsis_adip <- imap(pops_meta_dfs_adip, ~ join_gsis_data(.x, gsis_types, convert_numeric = TRUE))
```

```{r}
# Perform partial correlations
out_panc_long <- partial_ppcor_over_list(
  pops_list      = pops_with_gsis_panc,
  analyte_groups = analyte_groups,
  gsis_groups    = gsis_groups,
  tissue_label   = "Pancreas",
  gsis_suffix    = FALSE,            
  method         = "kendall",
  fdr_scope      = "within",
  symmetric      = FALSE,
  donor_col      = "DONOR"
)

out_adip_long <- partial_ppcor_over_list(
  pops_list      = pops_with_gsis_adip,
  analyte_groups = analyte_groups,
  gsis_groups    = gsis_groups,
  tissue_label   = "Adipose",
  gsis_suffix    = FALSE,            
  method         = "kendall",
  fdr_scope      = "within",
  symmetric      = FALSE,
  donor_col      = "DONOR"
)

out_panc_wide <- out_panc_long %>%
  dplyr::mutate(r_ci = sprintf("%.2f [%.2f, %.2f]", r, r_lower, r_upper)) %>%
  dplyr::select(var1, var2, tissue, pollutant_class, gsis_type,
                adjustment, r, r_ci, p, p_adj, n) %>% 
  tidyr::pivot_wider(
    names_from  = adjustment,
    values_from = c(r_ci, r, p, p_adj, n),
    names_glue  = "{.value}_{adjustment}"
  )

out_adip_wide <- out_adip_long %>%
  dplyr::mutate(r_ci = sprintf("%.2f [%.2f, %.2f]", r, r_lower, r_upper)) %>%
  dplyr::select(var1, var2, tissue, pollutant_class, gsis_type,
                adjustment, r, r_ci, p, p_adj, n) %>% 
  tidyr::pivot_wider(
    names_from  = adjustment,
    values_from = c(r_ci, r, p, p_adj, n),
    names_glue  = "{.value}_{adjustment}"
  )
```

```{r}
# Export dataframes
# library(writexl)
# 
# write_xlsx(
#   list(
#     panc_partial_corr = out_panc_wide,
#     adip_partial_corr = out_adip_wide
#   ),
#   path = "2025-08-25_partial_correlation_results.xlsx"
# )
```

# Session Info

```{r}
sessionInfo()
```

